### 2022-08-22 iros.tex
First commit with the draft of the paper for IROS.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Equilivest: A Robotic Vest to improve Human Balance Rehabilitation*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Franco Paviotti}
\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
\textit{Instituto Tecnológico de Buenos Aires}\\
Buenos Aires, Argentina \\
fpaviotti@itba.edu.ar}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Esteban Buniak}
\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
\textit{Instituto Tecnológico de Buenos Aires}\\
Buenos Aires, Argentina \\
fpaviotti@itba.edu.ar}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Rodrigo Ramele}
\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
\textit{Instituto Tecnológico de Buenos Aires}\\
Buenos Aires, Argentina \\
fpaviotti@itba.edu.ar}
\and
\IEEEauthorblockN{4\textsuperscript{th} Juan Miguel Santos}
\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
\textit{Instituto Tecnológico de Buenos Aires}\\
Buenos Aires, Argentina \\
fpaviotti@itba.edu.ar}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
\textit{Instituto Tecnológico de Buenos Aires}\\
Buenos Aires, Argentina \\
fpaviotti@itba.edu.ar}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
\textit{Instituto Tecnológico de Buenos Aires}\\
Buenos Aires, Argentina \\
fpaviotti@itba.edu.ar}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2022-08-22 iros.tex
Update with a raw version.  Adding all the references.

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+Stroke is a devastanting disease that affects bla bla bla.
+It has been shown that neurofeedback can help patients to regain lost motor activity and recover functionality.
+In this work, we are proposing a device that help patients by augmentation sensory sensation and pinning information to certain patterns in gait.
+We are presenting results from surveys to patient's caregivers, patients and medical personal.
+We are presenting the experimentation paradigm, and the robotic device that we created to help the patient.
 \end{abstract}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
 
-\section{Ease of Use}
+The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.
 
-\subsection{Maintaining the Integrity of the Specifications}
+\section{Materials and Methods}
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\subsection{Underlying hypothesis}
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\begin{itemize}
+\item Controlamos que la posición del IMU no supere un umbral, y si lo hace vibra el motor.
+\item Intentamos predecir una situación de caída y generar un alerta antes de que ocurra.
+\item Hacemos un pacemaker.  Es decir una estimulación sincrónica asociada a la detección de un podómetro.
+\end{itemize}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\subsection{Robotic Device Vest}
+How does it work, how is the detection of IMU working
+Internet of Robotic Things.
+Arduino
+
+\subsection{Experimental Design}
+How does it work, how is the detection of IMU working
+Internet of Robotic Things.
+Arduino
 
@@
 
+\section*{Results}
+\section*{Discussion}
+\section*{Conclusion}
 \section*{Acknowledgment}
@@
 
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
+\bibliographystyle{IEEEtran}
+\bibliography{iros}
+
 \vspace{12pt}

### 2022-08-29 iros.tex
Update.  General layout almost ready.

@@
 
-\title{Equilivest: A Robotic Vest to improve Human Balance Rehabilitation*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
+\title{Equilivest: A Robotic Vest to aid in Post-Stroke Human Balance Rehabilitation
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \author{\IEEEauthorblockN{1\textsuperscript{st} Franco Paviotti}
-\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
+\IEEEauthorblockA{\textit{Bioingeniería} \\
 \textit{Instituto Tecnológico de Buenos Aires}\\
@@
 Buenos Aires, Argentina \\
-fpaviotti@itba.edu.ar}
+ebuniak@itba.edu.ar}
 \and
@@
 Buenos Aires, Argentina \\
-fpaviotti@itba.edu.ar}
+rramele@itba.edu.ar}
 \and
@@
 \IEEEauthorblockA{\textit{Ingeniería en Informática} \\
-\textit{Instituto Tecnológico de Buenos Aires}\\
-Buenos Aires, Argentina \\
-fpaviotti@itba.edu.ar}
+\textit{UNAHUR}\\
+Hurlingham, Argentina \\
+jsantos@gmail.com}
 \and
@@
 
+Brain stroke is a devastating disease.
+It affects worldwide population and is the main cause of disabilities worldwide.
+Disabilities related to stroke can affect motor pathways, and may lead to several motor disability disorders.
+Hence, as early as possible the rehabilitation can be put into place, better the outcome that can be obtained by the treatment.
+
+Strong evidence suggests that neuroplasticity can be enhanced by neural rehabilitation~\cite{Albert.etal2012}.
+These procedures are aimed to relearn movements that can trigger new pathway generation which reroute, or even completely replace, those pathways that were damaged by the stroke.
+Neurorehabilitation procedures are performed by a group of interdisciplinary care givers and technicians.
+Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning has appear as an alternative treatment to increase neuralplasticitly, in the form of Wearable devices-based biofeedback rehabilitation (WDBR) home rehabilitation, or even daily use\cite{Peake.etal2018}.
+Authors found evidence that biofeedback can indeed help rehabilitation procedures.
+
+This work relies on the following idea:  the addition of an independent and new signal, that can be assimilated as an extrasensory input, could  provides extra information which could improve dynamic balance performance on stroke patients which may have yet insufficiency to deal properly with walking.
+The idea is that we have now the ability to provide meaningful balance information with hardware and software that can provide this extra signal in the form of any form of stimulation, for instance vibrotactile.
+
+We are presenting here the development of a device which is grounded on this idea, and is aiming to help a post-stroke patient with a dynamic balance problem as a case study.
+This is implemented with a smart-vest~\cite{Brandebusemeyer.etal2021}, which we will call, equilivest, that can detect some particular situation and implement in a way to fix one particular problem.
+We aim to provide motor learning, which means that you need to provide a fading vibrotactile feedback, and that the signal needs to be provided in a way which is less conscious as possible.
+The device is based on the idea to promote plasticity by giving her vibrotactile stimulation based on kinematic and dynamics measurements.
+The idea is to exploits these ideas from neurofeedback that we can create "external" sensors by providing some form of vibrotactile stimulation on her belly and link that stimulation to some form of measurements from IMUs (inertial sensors).
+
 The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.
+
+Section presents the case study.
+Next section presents the underlying clinical hypothesis that this work is trying to promote.
+Finally section this and that present the experimental design.
+Results are presented on the next section, and this work concludes with discussion and conclussion.
 
@@
 
+\subsection{Single Patient Case Study}
+
+Patient is a 31 years old female, perfectly healthy, who suffered an acute brainstem stroke after giving birth  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which was somehow facilitated by pregnancy or puerperium~\cite{Porras.etal2017}.
+Patient was in coma for around 2 months, after that unable to walk, move, talk or swallow.
+After two years of intensive rehabilitation, Patient managed to recover significantly, including from dysphagia, which were very important in order to remove the feeding tube allowing her to start speech recovering.
+
+After 24 months since event, the patient, was discharged from hospital and only maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related with dynamic walking balance problems.
+Patient achieved higher index scores in static balance tests and is fully able to hip-balance and ankle-balance.
+Patient has recovered muscle in her legs and can perform lower-limb workouts without problems.
+Her vision is normal.
+Somatosensorial system is optimal on foot sole.
+Tests performed to verify proprioceptive system were successfully passed.
+
+However, when Patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight) or with other people moving around, she is unable to keep up with the pace of the gait and falls frequently.
+This is consistent, under these three situations.
+Nowadays, the patient can walk with a Canadian cane or a non-actuated walking helper which she is hesitant to use, both.
+
 \subsection{Underlying hypothesis}
 
+Human balance is composed of a complex interaction of different subsystems, which includes somatosensorial information, vestibular system, visual information, which is later processed in different networks of the Central Nervous System, and actuated by motor pathways at many different scales.
+
+Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey} show the results of the surveys performed on the Patient and their main Rehabilitaion caregivers.
+Using the results from the surveys, we postulate three different systems that could benefit from the introduction of an external signal in the form of biofeedback that can aid in rehabilitation procedures.
+
+%Bradykinesia: due to the slow speech.
+%Unusual gait
+%Dysmetria (visual?) (ataxia?)
+
 \begin{itemize}
-\item Controlamos que la posición del IMU no supere un umbral, y si lo hace vibra el motor.
-\item Intentamos predecir una situación de caída y generar un alerta antes de que ocurra.
-\item Hacemos un pacemaker.  Es decir una estimulación sincrónica asociada a la detección de un podómetro.
+\item Vestibular information on fusion of vestibular information
+\item Bradykinesia: the processing speed required to effectively perform the processing and actuation is not enough.
+\item Unusual gait
 \end{itemize}
 
+Based on the surveys and the information provided by caregivers there seems not to be any somatosensorial deficit\cite{cite}.
+
 \subsection{Robotic Device Vest}
+Description of the system.
 How does it work, how is the detection of IMU working
@@
 
+\textbf{Why only vibrotactile stimulation and not auditory stimulation}
+
 \subsection{Experimental Design}
-How does it work, how is the detection of IMU working
-Internet of Robotic Things.
-Arduino
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+Three experiments were designed in order to test each one of the hypothesis.  All the experiments were approved by the ITBA University ethical committee.  Participants were recruited voluntarily.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
+%\begin{itemize}
+%\item Controlamos que la posición del IMU no supere un umbral, y si lo hace vibra el motor.
+%\item Intentamos predecir una situación de caída y generar un alerta antes de que ocurra.
+%\item Hacemos un pacemaker.  Es decir una estimulación sincrónica asociada a la detección de un podómetro.
+%\end{itemize}
+
+\subsubsection{Vestibular Feedback}
+
+The underlying idea is that signals from IMU can be feed back to the patient by vibrotactile stimulation on their belly.
+The hypothesis is that if there is a vestibular problem that forbids the patient to receive or evaluate the vestibular information appropriately, this external signal can be available for the patient to integrate it into the dynamic balance integration.
+
+In order to test it, 5 healthy participants are going to be recruited to simulate falling breakpoint conditions on the IMU information.
+Participants wear the vest and perform a forward walking exercise with the upper-trunk leaned forward at different angles progresively until they can no longer cope with the unbalance situation without stepping forward.
+
+Afterward, the experiment will be repeated with the 5 participants activating the vibrotactile stimulation which will map progressively the inclination angle.
+Hence it will provide an extra signal that can give a accurate information in relation to the stability of the upper-trunk in relation to the walking gait.
+
+\subsubsection{Bradykinesia: Fall prediction due to insufficient speed of step}
+
+All the IMU information represent a multichannel time series.  Hence, it can be used to predict a falling situation.
+
+In this case, 5 healthy participants perform 20 controlled falls over gym mats.
+
+(3) Ver en base a la encuesta como se da la situación de caída más común que Paula relata, en base a lo que ella manifiesta.
+Entonces lo que hacemos es tomamos 5 sujetos y los hacemos caer 5 veces cada uno sobre la colchoneta (o 10 o 20 x sujeto, lo que más puedas).
+Con estos datos, que son series de tiempo de 6 variables, intetamos ver si con un modelo de ML podemos predecir el momento de la caída simulada de cada uno de ellos y ANTICIPARNOS .
+La idea entonces es que suene el motor cuando el sistema detecta con antelación que puede venir una caída inminente.
+Aca se muestra el accuracy en la detección de la caída en los datos recabados.
+
+10 participants simulating falls.
+
+\subsubsection{Gait Pacemaker}
+
+This is a gait pacemaker coupled with a podometer.  It has been showed that gait synchronization with music achieved better effect \cite{Roerdink.etal2007}.
+
+(4) En este caso, lo que hacemos es armar un gráfico de gait y lo que hace el dispositivo es detectar un punto en el ciclo y vibrar de forma recurrente, como un marca paso, basado en un podómetro.
+En este caso, tomás 5 personas las hacés caminar, determinás cómo son esas curvas y accionás el motor siempre en el mismo momento.
+Lo que mostramos son los gráficos y el momento donde se dispara la estimulación.
+
+%\subsection{Abbreviations and Acronyms}\label{AA}
+%Define abbreviations and acronyms the first time they are used in the text, 
+%even after they have been defined in the abstract. Abbreviations such as 
+%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
+%abbreviations in the title or heads unless they are unavoidable.
+%
+%\subsection{Units}
+%\begin{itemize}
+%\item Use either SI (MKS) or CGS as primary units.
 (SI units are encouraged.) English units may be used as secondary units (in parentheses).
 An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
+%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
 This often leads to confusion because equations do not balance dimensionally.
 If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
+%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
 Spell out units when they appear in text: ``.
@@
 a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
+%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+%\end{itemize}
+%
+%\subsection{Equations}
+%Number equations consecutively. To make your 
+%equations more compact, you may use the solidus (~/~), the exp function, or 
+%appropriate exponents. Italicize Roman symbols for quantities and variables, 
+%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
+%sign. Punctuate equations with commas or periods when they are part of a 
+%sentence, as in:
+%\begin{equation}
+%a+b=\gamma\label{eq}
+%\end{equation}
+%
+%Be sure that the 
+%symbols in your equation have been defined before or immediately following 
+%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
+%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+%
+%\subsection{\LaTeX-Specific Advice}
+%
+%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
+%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
+%to combine sections, add equations, or change the order of figures or
+%citations without having to go through the file line by line.
+%
+%Please don't use the \verb|{eqnarray}| equation environment. Use
+%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
+%environment leaves unsightly spaces around relation symbols.
+%
+%Please note that the \verb|{subequations}| environment in {\LaTeX}
+%will increment the main equation counter even when there are no
+%equation numbers displayed. If you forget that, you might write an
+%article in which the equation numbers skip from (17) to (20), causing
+%the copy editors to wonder if you've discovered a new method of
+%counting.
+%
+%{\BibTeX} does not work by magic. It doesn't get the bibliographic
+%data from thin air but from .bib files. If you use {\BibTeX} to produce a
+%bibliography you must send the .bib files. 
+%
+%{\LaTeX} can't read your mind. If you assign the same label to a
+%subsubsection and a table, you might find that Table I has been cross
+%referenced as Table IV-B3. 
+%
+%{\LaTeX} does not have precognitive abilities. If you put a
+%\verb|\label| command before the command that updates the counter it's
+%supposed to be using, the label will pick up the last counter to be
+%cross referenced instead. In particular, a \verb|\label| command
+%should not go before the caption of a figure or a table.
+%
+%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
+%will not stop equation numbers inside \verb|{array}| (there won't be
+%any anyway) and it might stop a wanted equation number in the
+%surrounding equation.
+%
+%\subsection{Some Common Mistakes}\label{SCM}
+%\begin{itemize}
+%\item The word ``data'' is plural, not singular.
+%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
+%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
 When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
@@
 (A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
+%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
+%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
+%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
+%\item Do not confuse ``imply'' and ``infer''.
+%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
+%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
+%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+%\end{itemize}
+%An excellent style manual for science writers is \cite{b7}.
+%
+%\subsection{Authors and Affiliations}
+%\textbf{The class file is designed for, but not limited to, six authors.} A 
+%minimum of one author is required for all conference articles. Author names 
+%should be listed starting from left to right and then moving down to the 
+%next line. This is the author sequence that will be used in future citations 
+%and by indexing services. Names should not be listed in columns nor group by 
+%affiliation. Please keep your affiliations as succinct as possible (for 
+%example, do not differentiate among departments of the same organization).
+%
+%\subsection{Identify the Headings}
+%Headings, or heads, are organizational devices that guide the reader through 
+%your paper. There are two types: component heads and text heads.
+%
+%Component heads identify the different components of your paper and are not 
+%topically subordinate to each other. Examples include Acknowledgments and 
+%References and, for these, the correct style to use is ``Heading 5''. Use 
+%``figure caption'' for your Figure captions, and ``table head'' for your 
+%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
+%style (in this case, italic) in addition to the style provided by the drop 
+%down menu to differentiate the head from the text.
+%
+%Text heads organize the topics on a relational, hierarchical basis. For 
+%example, the paper title is the primary text head because all subsequent 
+%material relates and elaborates on this one topic. If there are two or more 
+%sub-topics, the next level head (uppercase Roman numerals) should be used 
+%and, conversely, if there are not at least two sub-topics, then no subheads 
+%should be introduced.
+%
+%\subsection{Figures and Tables}
+%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
+%bottom of columns. Avoid placing them in the middle of columns. Large 
+%figures and tables may span across both columns. Figure captions should be 
+%below the figures; table heads should appear above the tables. Insert 
+%figures and tables after they are cited in the text. Use the abbreviation 
+%``Fig.~\ref{fig}'', even at the beginning of a sentence.
+%
+%\begin{table}[htbp]
+%\caption{Table Type Styles}
+%\begin{center}
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+%\cline{2-4} 
+%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+%\hline
+%copy& More table copy$^{\mathrm{a}}$& &  \\
+%\hline
+%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+%\end{tabular}
+%\label{tab1}
+%\end{center}
+%\end{table}
+%
+%\begin{figure}[htbp]
+%\centerline{\includegraphics{fig1.png}}
+%\caption{Example of a figure caption.}
+%\label{fig}
+%\end{figure}
+%
+%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
+%rather than symbols or abbreviations when writing Figure axis labels to 
+%avoid confusing the reader. As an example, write the quantity 
+%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
+%units in the label, present them within parentheses. Do not label axes only 
+%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
+%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
+%quantities and units. For example, write ``Temperature (K)'', not 
+%``Temperature/K''.
 
 \section*{Results}
+
+(1) Se muestran entonces esos dos gráficos promediados de cada uno de los 5 sujetos (10 series, 5 sin el motor, 5 con el motor).
+
+(2) Se muestra los gráficos de las series de tiempo offline de los datos analizados y como el sistema online de predicción acierta justamente en anticipar la caída.
+(Esto es probablmente desde software lo más complejo).
+
+(3) Este caso probablemente sea el que requiera más experimentación sobre Paula en sí misma.
+La idea acá es tener los gráficos promediados de GAIT, que son todos cíclicos, de dos de las variables cualquiera del IMU que formen un ciclo, y ver que hay un patrón común que se da más o menos para las personas healthy.
+En base a eso, luego la idea es probar si con Paula ese patrón CAMBIA.
+A partir de que vemos si cambia hay que ver donde cambia y en ese punto meter el pacemaker.
+
 \section*{Discussion}
+
 \section*{Conclusion}
+
+This device used as a testbed can be extended easily to provide biofeedback which also aim to increase the effectiveness of rehabilitation procedures~\cite{Bowman2021}.
+
 \section*{Acknowledgment}
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+%The preferred spelling of the word ``acknowledgment'' in America is without 
+%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+%acknowledgments in the unnumbered footnote on the first page.
 
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+%Please number citations consecutively within brackets \cite{b1}. The 
+%sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+%number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+%the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+%
+%Number footnotes separately in superscripts. Place the actual footnote at 
+%the bottom of the column in which it was cited. Do not put footnotes in the 
+%abstract or reference list. Use letters for table footnotes.
+%
+%Unless there are six authors or more give all authors' names; do not use 
+%``et al.''. Papers that have not been published, even if they have been 
+%submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+%that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+%Capitalize only the first word in a paper title, except for proper nouns and 
+%element symbols.
+%
+%For papers published in translation journals, please give the English 
+%citation first, followed by the original foreign-language citation \cite{b6}.
 
@@
 
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
+%
+%\vspace{12pt}
+%\color{red}
+%IEEE conference templates contain guidance text for composing and formatting conference papers.
 Please ensure that all template text is removed from your conference paper prior to submission to the conference.

### 2022-09-11 iros.tex
Intro and the general layout ready.

@@
 
-\title{Equilivest: A Robotic Vest to aid in Post-Stroke Human Balance Rehabilitation
+\title{Equilivest: A Robotic Vest to aid in Post-Stroke Dynamic Human Balance Rehabilitation
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \begin{abstract}
-Stroke is a devastanting disease that affects bla bla bla.
-It has been shown that neurofeedback can help patients to regain lost motor activity and recover functionality.
-In this work, we are proposing a device that help patients by augmentation sensory sensation and pinning information to certain patterns in gait.
-We are presenting results from surveys to patient's caregivers, patients and medical personal.
-We are presenting the experimentation paradigm, and the robotic device that we created to help the patient.
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Stroke, Balance, Rehabilitation, Biofeedback, Vibrotactile
 \end{IEEEkeywords}
@@
 
-Brain stroke is a devastating disease.
-It affects worldwide population and is the main cause of disabilities worldwide.
-Disabilities related to stroke can affect motor pathways, and may lead to several motor disability disorders.
-Hence, as early as possible the rehabilitation can be put into place, better the outcome that can be obtained by the treatment.
+Brain stroke is a devastating disease, that affects world population and is the main cause of disabilities worldwide~\cite{Caplan.etal2023}.
+Disabilities related to stroke can affect motor pathways, and may lead to several motor function disorders.
+One important aspect of motor function is balance which is the ability to control the center of mass of the body inside the base support provided by the lower limb.
+Stroke can affect dynamic balance as well,  which is manifested while walking and that affect autonomy, independence and is an important factor in activities of daily living (ADL) particularly for young patients~\cite{Afrasiabifar.etal2020,Donato.etal2016}.
 
-Strong evidence suggests that neuroplasticity can be enhanced by neural rehabilitation~\cite{Albert.etal2012}.
+% As early as possible the rehabilitation can be put into place, better the outcome that can be obtained by the treatment.
+
+Strong evidence suggests that neuroplasticity can be enhanced by neural rehabilitation~\cite{DeAngelis.etal2021,Albert.etal2012}.
 These procedures are aimed to relearn movements that can trigger new pathway generation which reroute, or even completely replace, those pathways that were damaged by the stroke.
-Neurorehabilitation procedures are performed by a group of interdisciplinary care givers and technicians.
-Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning has appear as an alternative treatment to increase neuralplasticitly, in the form of Wearable devices-based biofeedback rehabilitation (WDBR) home rehabilitation, or even daily use\cite{Peake.etal2018}.
-Authors found evidence that biofeedback can indeed help rehabilitation procedures.
+Neurorehabilitation procedures are performed by a group of interdisciplinary caregivers and technicians.
+Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning have appeared as an alternative treatment to increase neuralplasticitly.
+These are in the form of Wearable devices-based biofeedback rehabilitation (WDBR)~\cite{Peake.etal2018} or more advanced robotic rehabilitation gait devices~\cite{Zhao.etal2022,Peshkin.etal2005,Tong.etal2006}.
 
-This work relies on the following idea:  the addition of an independent and new signal, that can be assimilated as an extrasensory input, could  provides extra information which could improve dynamic balance performance on stroke patients which may have yet insufficiency to deal properly with walking.
-The idea is that we have now the ability to provide meaningful balance information with hardware and software that can provide this extra signal in the form of any form of stimulation, for instance vibrotactile.
+%This published evidence emphasizes that this biofeedback can indeed enhance the results of rehabilitation procedures.
 
-We are presenting here the development of a device which is grounded on this idea, and is aiming to help a post-stroke patient with a dynamic balance problem as a case study.
-This is implemented with a smart-vest~\cite{Brandebusemeyer.etal2021}, which we will call, equilivest, that can detect some particular situation and implement in a way to fix one particular problem.
-We aim to provide motor learning, which means that you need to provide a fading vibrotactile feedback, and that the signal needs to be provided in a way which is less conscious as possible.
-The device is based on the idea to promote plasticity by giving her vibrotactile stimulation based on kinematic and dynamics measurements.
-The idea is to exploits these ideas from neurofeedback that we can create "external" sensors by providing some form of vibrotactile stimulation on her belly and link that stimulation to some form of measurements from IMUs (inertial sensors).
+The working hypothesis is as follows:  the addition of an independent and new peripheral therapeutic signal, that can be assimilated as an extrasensory input,  could improve dynamic balance performance on stroke patients which may have yet insufficiency to deal properly with the complexities of walking.
+The idea is that we have now the ability to provide meaningful balance information with hardware and software that can provide this extra signal in the form of any form of stimulation, particularly vibrotactile feedback (VF).
+Although the effectiveness of biofeedback on static balance has been tackled extensively in the literature, works dealing with dynamic balancing problems have been negligible.
 
-The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.
+This work presents the development of a device which is grounded on this idea, and aims to help a post-stroke patient with a remaining dynamic balance problem, and present it as a case study.
+The proposed development is implemented as a smart-vest~\cite{Brandebusemeyer.etal2021}, which we will call, equilivest, that address three possible clinical hypothesis of the underlying problem.
+We aim to provide motor learning, meaning to provide a fading vibrotactile feedback signal which is as less conscious as possible~\cite{Donato.etal2016}.
+The device aims to promote plasticity by providing timing vibrotactile stimulation based on kinematic and dynamics measurements.
+
+%The idea is to exploits these ideas from neurofeedback that we can create "external" sensors by providing some form of vibrotactile stimulation on her belly and link that stimulation to some form of measurements from IMUs (inertial sensors).
+
+%The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.
 
 Section presents the case study.
-Next section presents the underlying clinical hypothesis that this work is trying to promote.
-Finally section this and that present the experimental design.
-Results are presented on the next section, and this work concludes with discussion and conclussion.
+Next section summarize the results of the interviews and surveys performed by the patient, their family and professional caregivers.
+Based on the analyze of the data, the next section presents the underlying clinical hypothesis.
+Section A describes the vest details and architecture.
+The experimental design protocol is expounded in Section B.
+Preliminary results are presented on the next section, and this work concludes with discussion and conclusion.
 
@@
 
-Patient is a 31 years old female, perfectly healthy, who suffered an acute brainstem stroke after giving birth  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which was somehow facilitated by pregnancy or puerperium~\cite{Porras.etal2017}.
-Patient was in coma for around 2 months, after that unable to walk, move, talk or swallow.
+Patient is a 31 years old female, perfectly healthy, who suffered an acute brainstem stroke after giving birth  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which was likely affected by pregnancy or puerperium~\cite{Porras.etal2017}.
+Patient was in coma for around 2 months, and after that unable to walk, move, talk or swallow.
 After two years of intensive rehabilitation, Patient managed to recover significantly, including from dysphagia, which were very important in order to remove the feeding tube allowing her to start speech recovering.
@@
 After 24 months since event, the patient, was discharged from hospital and only maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related with dynamic walking balance problems.
-Patient achieved higher index scores in static balance tests and is fully able to hip-balance and ankle-balance.
-Patient has recovered muscle in her legs and can perform lower-limb workouts without problems.
+The patient achieved satisfactory index scores in static balance tests and is fully able to perform hip-balance and ankle-balance.
+She has recovered muscle in her legs and can perform lower-limb exercises.
 Her vision is normal.
-Somatosensorial system is optimal on foot sole.
 Tests performed to verify proprioceptive system were successfully passed.
 
-However, when Patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight) or with other people moving around, she is unable to keep up with the pace of the gait and falls frequently.
-This is consistent, under these three situations.
+However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or when walking concentration fades, she is unable to keep up with the pace of the gait and falls frequently.
+This is consistent, under these situations.
 Nowadays, the patient can walk with a Canadian cane or a non-actuated walking helper which she is hesitant to use, both.
+
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}[!t]{|c|c|}
+\hline
+Question & Avg. answer \\
+\hline
+Podes describir cómo y cuándo se expresa la perdida del equilibrio y su proceso?
+- Esta pregunta nos servirá para determinar con mayor precisión los métodos de sensado y alarma a desarrollar  & Cuando estoy cansada, distraída o muy nerviosa\\
+\hline
+¿Siempre se desarrolla de la misma manera? - Con esta pregunta queremos profundizar sobre la anterior con el objetivo de una mejor comprensión &  Si \\
+\hline
+¿Cuál? Si la respuesta fue no, deje sin contestar  & Me desequilibro\\
+\hline
+¿Podés evidenciar cuando estas por empezar a perder el equilibrio? - Con esta pregunta intentamos conocer un fenómeno que permita detectar el principio de caída & Si \\
+\hline
+Si la respuesta fue si ¿Qué sentís? & Un poco no siempre siento inestabilidad previo  \\
+\hline
+¿Con qué frecuencia usas el andador? - Puede seleccionar mas de una opción. Así nos ayudará a entender mejor el cuadro & Solo fuera de casa \\
+\hline
+¿Existe algún denominador común en las caídas?
+- La presencia de este sería importantísima para  un fenómeno o señal a medir y caracterizar que sería muy útil para la detección del principio de caídas.
+Si hay algo que siempre se repite podríamos enfocarnos en detectar eso.
+& Si \\
+\hline\\
+¿Cuál? Si la respuesta fue "No" deje la respuesta en blanco & Lo que anteriormente dije estoy cansada o distraída o nerviosa  \\
+\hline
+¿Cómo estás trabajando la recuperación hoy por hoy? - Con esta pregunta buscamos conocer el estado de situación y trabajo actual & Fortalecimiento de músculos   \\
+\hline
+¿Hay algo más que desees comentar o expresar? & No uso andador es un bastón canadiense. 
+Ahora me doy cuenta antes que me voy a caer, pero queda poco para evitarlo.   \\
+\hline
+\end{tabular}
+\caption{table}{Answers to survey questions.}
+\label{tab:alpi_q_table_1}
+\end{center}
+\end{table*}
+
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}[!t]{|c|c|}
+\hline
+Question & Avg. answer \\
+\hline
+¿Cuál es la razón de la pérdida del equilibrio en la paciente? - Esta pregunta nos permite conocer la opinión de los profesionales e interiorizarnos en el caso.  & Lesión en el tronco del encéfalo\\
+\hline
+¿Podes describir cómo y cuándo se expresa la perdida del equilibrio y su proceso?
+- Con la descripción podemos comprender como y en que circunstancias se desencadena el fenómeno de la caída y conocer mejor el caso.
+&  La pérdida del equilibrio se expresa en el inicio y durante la marcha.
+cuando se detiene también.
+Camina con compensación visual y cuando quita la vista el suelo (ej mira para el costado aumenta la inestabilidad) Realiza una marcha sin el automatismo habitual.
+Le demanda mucha concentracion.
+\\
+\hline
+¿ La paciente puede caminar sin un dispositivo de tipo ayuda marcha?
+De ser así, ¿Bajo que circunstancias?
+- Conociendo mejor la situación actual podemos tomar mejores decisiones en cuanto a como posicionar sensores y medir.
+& Solo de manera  terapéutica.
+habitualmente la trabajamos con máxima supervisión.\\
+\hline
+¿Presenta una pérdida de fuerza muscular que dificulte el caminar?
+- Esta pregunta permite conocer el caso en mayor detalle  con propiedad para evitar adelantarnos a hipótesis de trabajo erróneas.
+& No \\
+\hline
+¿Presenta dismetría?
+- Nuevamente queremos adelantarnos a hipótesis erróneas a la hora de decidir el método de sensado y procesamiento de las señales.
+La longitud o duración de los movimientos puede usarse como un indicador para nosotros, como también asi los ritmos.
+& Si \\
+\hline
+¿Presenta temblores?  - En caso de presentar temblores estos se verán reflejados en las señales y es útil tenerlo en cuenta ya que caracterizará a nuestra señal. & No \\
+\hline
+¿Presenta alteraciones en la marcha en instantes previos a la caída?
+- En caso de existir algún impulso inicial que podamos sensar o medir de forma indirecta podemos anticiparnos a la perdida del equilibrio en las señales.
+& Si \\
+\hline\\
+¿Cuáles? Si la respuesta fue "No" deje en blanco & Fallas las reacciones de tobillo y cadera \\
+\hline
+¿Sufrió alteraciones en la sensibilidad profunda?
+- Existe un trabajo previo en la Universidad de Buenos Aires que usa un método de sensado orientado a la presión de la pisada.
+Esto puede orientarnos en otro sentido en el sensado y estimulación.
+& No  \\
+\hline
+Antes de perder el equilibrio, ¿Trastabilla?¿Acelera la marcha?
+-  Al igual que en otras preguntas buscamos obtener información extra para el  procesamiento de las señales y detección del principio de caída.
+Estos fenómenos pueden medirse o detectarse y evidenciarían el inicio de una posible caída.
+& Otro síntoma  \\
+\hline
+Si la respuesta fue 'Otro síntoma' ¿Cuál? - En caso contrario deje sin responder & Reacción lenta \\
+\hline
+¿Presenta algún tipo de marcha patológica? -la caracterización del caso permite decidir formas y métodos de sensado y procesamiento. & Si  \\
+\hline
+¿Cuál? Si la respuesta fue "No" deje la respuesta en blanco & Marcha Atáxica \\
+\hline
+¿Existe algún denominador común en las caídas?
+- La presencia de este sería importantisima para  un fenómeno o señal a medir y caracterizar que sería muy útil para la detección del principio de caídas.
+Si hay algo que siempre se repite podríamos enfocarnos en detectar eso.
+& Si \\
+\hline
+¿Cuál?
+Si la respuesta fue "No" deje la respuesta en blanco & El denominador es cuando deja de realizar la marcha de manera consciente.
+Por ejemplo, cuando camina y tiene que realizar alguna tarea que implique procesos cognitivo.
+Dual Task  \\
+\hline
+¿Se hizo un estudio de evaluación de marcha? - Esta pregunta podría aportar información suplementaria a preguntas anteriores que nos permiten conocer e interiorizarnos en el caso & No  \\
+\hline
+¿Se hizo evaluación de riesgo de caídas? - Esta pregunta puede aportar algo de información extra para el conocimiento del caso. & Si  \\
+\hline
+¿Hay alguna manera en que trabaje en la reeducación de la paciente?
+-  Quisiéramos conocer un poco mas la situación actual y las actividades que realiza la paciente para su recuperación.
+& Si a través de la reeducación del VOR,  facilitación del equilibrio estático y dinámico, entrenamiento del automatismo de la marcha con diferentes niveles de dificultad.
+\\
+\hline
+¿Hay algo mas que desee comentar o expresar?  & Mes a mes se evidencia una mejora, todavía no alcanza para que pueda caminar sin supervisión.  \\
+\hline
+\end{tabular}
+\caption{table}{Answers to survey questions.}
+\label{tab:alpi_q_table_1}
+\end{center}
+\end{table*}
+
+Based on the surveys and the information provided by caregivers there seems not to be any somatosensorial deficit~\cite{Donato.etal2016}. 
+There isn't any report of somatosensorial on foot sole.
 
@@
 
-Human balance is composed of a complex interaction of different subsystems, which includes somatosensorial information, vestibular system, visual information, which is later processed in different networks of the Central Nervous System, and actuated by motor pathways at many different scales.
+Human balance is composed of a complex interaction of different subsystems, which includes somatosensorial information, vestibular system and visual information as input sources.
+These are later processed in different networks of the Central Nervous System, and finally actuated by motor pathways at many different scales~\cite{Donato.etal2016}.
 
-Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey} show the results of the surveys performed on the Patient and their main Rehabilitaion caregivers.
-Using the results from the surveys, we postulate three different systems that could benefit from the introduction of an external signal in the form of biofeedback that can aid in rehabilitation procedures.
+We perform a series of surveys and interviews with the patient and their caregivers.  Main results are summarized in 
+Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey}.
+Based on the clinical history, the results from the surveys and interviews, we postulate three different potential clinical situations that could use the external signal in the form of biofeedback and could potentially aid in rehabilitation procedures.
 
@@
 \begin{itemize}
-\item Vestibular information on fusion of vestibular information
+\item Vestibular information or fusion of vestibular information
 \item Bradykinesia: the processing speed required to effectively perform the processing and actuation is not enough.
-\item Unusual gait
+\item Unusual gait: due to ataxic gait the movement is not normally regulated.
 \end{itemize}
-
-Based on the surveys and the information provided by caregivers there seems not to be any somatosensorial deficit\cite{cite}.
 
@@
 
-(3) Ver en base a la encuesta como se da la situación de caída más común que Paula relata, en base a lo que ella manifiesta.
+%(3) Ver en base a la encuesta como se da la situación de caída más común que Paula relata, en base a lo que ella manifiesta.
 Entonces lo que hacemos es tomamos 5 sujetos y los hacemos caer 5 veces cada uno sobre la colchoneta (o 10 o 20 x sujeto, lo que más puedas).
@@
 
-10 participants simulating falls.
-
 \subsubsection{Gait Pacemaker}
 
-This is a gait pacemaker coupled with a podometer.  It has been showed that gait synchronization with music achieved better effect \cite{Roerdink.etal2007}.
+This is a gait pacemaker coupled with a podometer.
+It has been showed that gait synchronization with music achieved better effect \cite{Roerdink.etal2007} and there are effect on gait trainer on patient \cite{Blicher.etal2009}.
+During this experiment 5 participants walked 5 meters distance.
+IMU information was obtained to derive standard diagrams of gait patterns.
+They were compared against those obtained for the patient under study.
+And it was determiend the exact moment when the deviation against the patient was greater and the VF was triggered upon that.
 
-(4) En este caso, lo que hacemos es armar un gráfico de gait y lo que hace el dispositivo es detectar un punto en el ciclo y vibrar de forma recurrente, como un marca paso, basado en un podómetro.
+%(4) En este caso, lo que hacemos es armar un gráfico de gait y lo que hace el dispositivo es detectar un punto en el ciclo y vibrar de forma recurrente, como un marca paso, basado en un podómetro.
 En este caso, tomás 5 personas las hacés caminar, determinás cómo son esas curvas y accionás el motor siempre en el mismo momento.
 Lo que mostramos son los gráficos y el momento donde se dispara la estimulación.
+
+\subsection{Participants}
+
+Participants are recruited voluntarily and the experiment is conducted anonymously in accordance with the declaration of Helsinki published by the World Health Organization.
+No monetary compensation is handed out and all participants agree and sign a written informed consent approved by the ITBA University Research Commission.
 

### 2022-09-12 iros.tex
Added details about the implementation.

@@
 \subsection{Robotic Device Vest}
-Description of the system.
-How does it work, how is the detection of IMU working
-Internet of Robotic Things.
-Arduino
+The whole vest system is made of, in a high level description, a battery shield, an esp8266 based arduino shield, an inertial measurement unit (MPU 6050) and a vibration motor to stimulate the patient.
+MPU 6050 uses the accelerometer and gyroscope data to get angular acceleration and measure pitch roll and yaw angles.
+Said angles are measured by calculation with the corresponding equations and processed with a complementary filter which relies 80\% in gyroscope data and 20\% in accelerometer data.
+This values will be sent in real time as packets to a UDP server and later visualized and exported by the server host for further processing.
+The whole system can be powered by power banks or a 18650 battery array.
 

### 2022-09-16 iros.tex
Almost the finished version.

--- 2022-08-29 iros.tex
@@
 
-\title{Equilivest: A Robotic Vest to aid in Post-Stroke Human Balance Rehabilitation
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{Equilivest: A Robotic Vest to aid in Post-Stroke Dynamic Balance Rehabilitation
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Franco Paviotti}
-\IEEEauthorblockA{\textit{Bioingeniería} \\
-\textit{Instituto Tecnológico de Buenos Aires}\\
-Buenos Aires, Argentina \\
-fpaviotti@itba.edu.ar}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Esteban Buniak}
-\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
-\textit{Instituto Tecnológico de Buenos Aires}\\
-Buenos Aires, Argentina \\
-ebuniak@itba.edu.ar}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Rodrigo Ramele}
-\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
-\textit{Instituto Tecnológico de Buenos Aires}\\
-Buenos Aires, Argentina \\
-rramele@itba.edu.ar}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Juan Miguel Santos}
-\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
-\textit{UNAHUR}\\
-Hurlingham, Argentina \\
-jsantos@gmail.com}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
-\textit{Instituto Tecnológico de Buenos Aires}\\
-Buenos Aires, Argentina \\
-fpaviotti@itba.edu.ar}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
-\textit{Instituto Tecnológico de Buenos Aires}\\
-Buenos Aires, Argentina \\
-fpaviotti@itba.edu.ar}
+\author{%
+Franco Paviotti$^{1}$, Esteban Buniak$^{2}$, Rodrigo Ramele$^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
+\thanks{$^{1}$F. Paviotti is with Bioengineering, Instituto Tecnológico de Buenos Aires
+                    Buenos Aires, Argentina
+        {\tt\small fpaviotti@itba.edu.ar}}%
+\thanks{$^{2}$E.Buniak is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires
+                    Buenos Aires, Argentina
+        {\tt\small ebuniak@itba.edu.ar}}%
+\thanks{$^{3}$R.Ramele is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires
+                    Buenos Aires, Argentina
+        {\tt\small rramele@itba.edu.ar}}%
+\thanks{$^{4}$O. Freixes is with the CINER Centro Integral de Neurorehabilitación,
+                    Buenos Aires, Argentina
+        {\tt\small orestesfreixes@gmail.com}}%
+\thanks{$^{5}$J.M. Santos is with the UNAHUR Universidad Nacional de Hurlingham,
+                    Buenos Aires, Argentina
+        {\tt\small juanmiguelsantos@gmail.com}}%
+%\thanks{*This work was not supported by any organization}% <-this % stops a space}
 }
+
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Franco Paviotti}
+%\IEEEauthorblockA{\textit{Bioingeniería} \\
+%\textit{Instituto Tecnológico de Buenos Aires}\\
+%Buenos Aires, Argentina \\
+%fpaviotti@itba.edu.ar}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Esteban Buniak}
+%\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
+%\textit{Instituto Tecnológico de Buenos Aires}\\
+%Buenos Aires, Argentina \\
+%ebuniak@itba.edu.ar}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Rodrigo Ramele}
+%\IEEEauthorblockA{\textit{Ingeniería en Informática} \\
+%\textit{Instituto Tecnológico de Buenos Aires}\\
+%Buenos Aires, Argentina \\
+%rramele@itba.edu.ar}
+%\and
+%\IEEEauthorblockN{4\textsuperscript{th} Juan Miguel Santos}
+%\IEEEauthorblockN{\textit{Ingeniería en Informática} \\
+%\textit{UNAHUR}\\
+%Hurlingham, Argentina \\
+%jsantos@gmail.com}
+%\and
+%\IEEEauthorblockN{5\textsuperscript{th} Orestes Freixes}
+%\IEEEauthorblockN{\textit{CINER} \\
+%\textit{Centro Integral de NeuroRehabilitación}\\
+%Buenos Aires, Argentina \\
+%orestesfreixes@gmail.com}
+%}
 
@@
 \begin{abstract}
-Stroke is a devastanting disease that affects bla bla bla.
-It has been shown that neurofeedback can help patients to regain lost motor activity and recover functionality.
-In this work, we are proposing a device that help patients by augmentation sensory sensation and pinning information to certain patterns in gait.
-We are presenting results from surveys to patient's caregivers, patients and medical personal.
-We are presenting the experimentation paradigm, and the robotic device that we created to help the patient.
+Stroke is a medical condition that can affect motor function, particularly dynamic balance.
+Biofeedback can aid in rehabilitaiton procedures which help patients to regain lost motor activity and recover functionality.
+In this work, we are presenting a smart-vest device that assist in rehabilitation procedures by providing feedback in the form of vibrotactile stimulation.
+Information provided by principal caregivers, family, patient in the form of surveys and interview, is used to derive potential clinical causal hypothesis and these are used to drive the experimentation paradigm, and the robotic smart-vest to aid in the whole procedure...
 \end{abstract}
@@
 
-Brain stroke is a devastating disease.
-It affects worldwide population and is the main cause of disabilities worldwide.
-Disabilities related to stroke can affect motor pathways, and may lead to several motor disability disorders.
-Hence, as early as possible the rehabilitation can be put into place, better the outcome that can be obtained by the treatment.
+Brain stroke is a devastating medical condition, that affects world population and is the main cause of disabilities worldwide~\cite{Caplan.etal2023}.
+Disabilities related to stroke can affect motor pathways, and may lead to several motor function disorders.
+One important aspect of motor function is balance which is the ability to control the center of mass of the body inside the base support provided by the lower limb~\cite{Bowman2021}.
+Stroke can affect dynamic balance as well,  which is manifested while walking, impairing autonomy and independence, important factors in Activities of Daily Living (ADL) particularly for young patients~\cite{Afrasiabifar.etal2020,Donato.etal2016}.
 
-Strong evidence suggests that neuroplasticity can be enhanced by neural rehabilitation~\cite{Albert.etal2012}.
-These procedures are aimed to relearn movements that can trigger new pathway generation which reroute, or even completely replace, those pathways that were damaged by the stroke.
-Neurorehabilitation procedures are performed by a group of interdisciplinary care givers and technicians.
-Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning has appear as an alternative treatment to increase neuralplasticitly, in the form of Wearable devices-based biofeedback rehabilitation (WDBR) home rehabilitation, or even daily use\cite{Peake.etal2018}.
-Authors found evidence that biofeedback can indeed help rehabilitation procedures.
+% As early as possible the rehabilitation can be put into place, better the outcome that can be obtained by the treatment.
 
-This work relies on the following idea:  the addition of an independent and new signal, that can be assimilated as an extrasensory input, could  provides extra information which could improve dynamic balance performance on stroke patients which may have yet insufficiency to deal properly with walking.
-The idea is that we have now the ability to provide meaningful balance information with hardware and software that can provide this extra signal in the form of any form of stimulation, for instance vibrotactile.
+Strong evidence suggests that neuroplasticity can be enhanced by neural rehabilitation~\cite{DeAngelis.etal2021,Albert.etal2012}.
+These procedures are aimed to relearn movements that can trigger new neural pathway generation which reroute, or even completely replace, those pathways that were damaged by the stroke.
+Neurorehabilitation procedures are performed by a group of interdisciplinary caregivers and technicians.
+Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning have appeared as an alternative treatment to increase neuralplasticity.
+These are in the form of Wearable devices-based biofeedback rehabilitation (WDBR)~\cite{Peake.etal2018} or more advanced robotic rehabilitation gait devices~\cite{Zhao.etal2022,Peshkin.etal2005,Tong.etal2006}.
 
-We are presenting here the development of a device which is grounded on this idea, and is aiming to help a post-stroke patient with a dynamic balance problem as a case study.
-This is implemented with a smart-vest~\cite{Brandebusemeyer.etal2021}, which we will call, equilivest, that can detect some particular situation and implement in a way to fix one particular problem.
-We aim to provide motor learning, which means that you need to provide a fading vibrotactile feedback, and that the signal needs to be provided in a way which is less conscious as possible.
-The device is based on the idea to promote plasticity by giving her vibrotactile stimulation based on kinematic and dynamics measurements.
-The idea is to exploits these ideas from neurofeedback that we can create "external" sensors by providing some form of vibrotactile stimulation on her belly and link that stimulation to some form of measurements from IMUs (inertial sensors).
+%This published evidence emphasizes that this biofeedback can indeed enhance the results of rehabilitation procedures.
 
-The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.
+Therefore, the addition of an independent and new peripheral therapeutic signal, that can be assimilated as an extrasensory input~\cite{Brandebusemeyer.etal2021},  could improve dynamic balance performance on post-stroke patients which may have yet insufficiency to deal properly with the complexities of walking.
+Meaningful balance information, in terms of timing and location, can provide this extra signal in any form of stimulation, particularly vibrotactile feedback (VF).
+Although the effectiveness of biofeedback on static balance has been studied more extensively in the literature~\cite{DeAngelis.etal2021}, to the best of our knowledge works dealing with dynamic balance problems while walking have been more scarce.
 
-Section presents the case study.
-Next section presents the underlying clinical hypothesis that this work is trying to promote.
-Finally section this and that present the experimental design.
-Results are presented on the next section, and this work concludes with discussion and conclussion.
+This work presents the development of a device which is grounded on this idea, and aims to help a post-stroke patient with a remaining dynamic balance problem, presenting it as a case study.
+The proposed development is implemented as a smart-vest~\cite{Brandebusemeyer.etal2021}, which we will call, \textit{Equilivest}, that address three possible clinical hypothesis of the underlying problem.
+We aim to provide motor learning, meaning to generate a fading compliant assist-as-needed vibrotactile feedback signal which is manifested to the patient as less conscious as possible~\cite{Srivastava.etal2016,Donato.etal2016}.
+The device aims to promote plasticity by producing timing vibrotactile stimulation based on kinematic and dynamics measurements.
+
+%The idea is to exploits these ideas from neurofeedback that we can create "external" sensors by providing some form of vibrotactile stimulation on her belly and link that stimulation to some form of measurements from IMUs (inertial sensors).
+
+%The form of validation procedures that is required in clinical settings\cite{Papastylianou.etal2016}.
+
+Section \ref{sec:case-study} presents the case study.
+Next section \ref{sec:hypothesis} summarize the results of the interviews and surveys performed by the patient, their family and professional caregivers, presenting the underlying clinical causal hypothesis.
+Section \ref{sec:vest} describes the vest details and architecture.
+The experimental design protocol is expounded in Section \ref{sec:experimental}.
+Preliminary results are presented on the next section, and this work concludes with discussion and conclusion.
 
@@
 
-\subsection{Single Patient Case Study}
+\subsection{Patient Case Study}
+\label{sec:case-study}
 
-Patient is a 31 years old female, perfectly healthy, who suffered an acute brainstem stroke after giving birth  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which was somehow facilitated by pregnancy or puerperium~\cite{Porras.etal2017}.
-Patient was in coma for around 2 months, after that unable to walk, move, talk or swallow.
-After two years of intensive rehabilitation, Patient managed to recover significantly, including from dysphagia, which were very important in order to remove the feeding tube allowing her to start speech recovering.
+Patient is a 31 years old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.
+The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.
+Patient was in coma for around 2 months, and after that unable to walk, move, talk or swallow.
+After two years of intensive rehabilitation, Patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.
 
-After 24 months since event, the patient, was discharged from hospital and only maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related with dynamic walking balance problems.
-Patient achieved higher index scores in static balance tests and is fully able to hip-balance and ankle-balance.
-Patient has recovered muscle in her legs and can perform lower-limb workouts without problems.
+After 24 months since event, the patient, was discharged from hospital and only maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related with dynamic balance problems while walking.
+The patient achieved satisfactory index scores in static balance tests and is able to perform static hip-balance and ankle-balance.
+She has recovered muscle in her legs and can perform lower-limb exercises.
 Her vision is normal.
-Somatosensorial system is optimal on foot sole.
-Tests performed to verify proprioceptive system were successfully passed.
 
-However, when Patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight) or with other people moving around, she is unable to keep up with the pace of the gait and falls frequently.
-This is consistent, under these three situations.
-Nowadays, the patient can walk with a Canadian cane or a non-actuated walking helper which she is hesitant to use, both.
+However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or while walking concentration fades, she is unable to keep up with the pace of the gait and the risk of fall increases.
+Nowadays, the patient walks freely unaided at home but requires a Canadian cane otherwise.
+
+%\begin{table*}[t]
+%\begin{center}
+%\begin{tabular}[!t]{|c|c|}
+%\hline
+%Question & Avg. answer \\
+%\hline
+%Podes describir cómo y cuándo se expresa la perdida del equilibrio y su proceso?
+- Esta pregunta nos servirá para determinar con mayor precisión los métodos de sensado y alarma a desarrollar  & Cuando estoy cansada, distraída o muy nerviosa\\
+%\hline
+%¿Siempre se desarrolla de la misma manera? - Con esta pregunta queremos profundizar sobre la anterior con el objetivo de una mejor comprensión &  Si \\
+%\hline
+%¿Cuál? Si la respuesta fue no, deje sin contestar  & Me desequilibro\\
+%\hline
+%¿Podés evidenciar cuando estas por empezar a perder el equilibrio? - Con esta pregunta intentamos conocer un fenómeno que permita detectar el principio de caída & Si \\
+%\hline
+%Si la respuesta fue si ¿Qué sentís? & Un poco no siempre siento inestabilidad previo  \\
+%\hline
+%¿Con qué frecuencia usas el andador? - Puede seleccionar mas de una opción. Así nos ayudará a entender mejor el cuadro & Solo fuera de casa \\
+%\hline
+%¿Existe algún denominador común en las caídas?
+- La presencia de este sería importantísima para  un fenómeno o señal a medir y caracterizar que sería muy útil para la detección del principio de caídas.
+Si hay algo que siempre se repite podríamos enfocarnos en detectar eso.
+& Si \\
+%\hline\\
+%¿Cuál? Si la respuesta fue "No" deje la respuesta en blanco & Lo que anteriormente dije estoy cansada o distraída o nerviosa  \\
+%\hline
+%¿Cómo estás trabajando la recuperación hoy por hoy? - Con esta pregunta buscamos conocer el estado de situación y trabajo actual & Fortalecimiento de músculos   \\
+%\hline
+%¿Hay algo más que desees comentar o expresar? & No uso andador es un bastón canadiense. 
+%Ahora me doy cuenta antes que me voy a caer, pero queda poco para evitarlo.   \\
+%\hline
+%\end{tabular}
+%\caption{table}{Answers to survey questions.}
+%\label{tab:alpi_q_table_1}
+%\end{center}
+%\end{table*}
+
+%\begin{table*}[t]
+%\begin{center}
+%\begin{tabular}[!t]{|c|c|}
+%\hline
+%Question & Avg. answer \\
+%\hline
+%¿Cuál es la razón de la pérdida del equilibrio en la paciente? - Esta pregunta nos permite conocer la opinión de los profesionales e interiorizarnos en el caso.  & Lesión en el tronco del encéfalo\\
+%\hline
+%¿Podes describir cómo y cuándo se expresa la perdida del equilibrio y su proceso?
+- Con la descripción podemos comprender como y en que circunstancias se desencadena el fenómeno de la caída y conocer mejor el caso.
+&  La pérdida del equilibrio se expresa en el inicio y durante la marcha.
+cuando se detiene también.
+Camina con compensación visual y cuando quita la vista el suelo (ej mira para el costado aumenta la inestabilidad) Realiza una marcha sin el automatismo habitual.
+Le demanda mucha concentracion.
+\\
+%\hline
+%¿ La paciente puede caminar sin un dispositivo de tipo ayuda marcha?
+De ser así, ¿Bajo que circunstancias?
+- Conociendo mejor la situación actual podemos tomar mejores decisiones en cuanto a como posicionar sensores y medir.
+& Solo de manera  terapéutica.
+habitualmente la trabajamos con máxima supervisión.\\
+%\hline
+%¿Presenta una pérdida de fuerza muscular que dificulte el caminar?
+- Esta pregunta permite conocer el caso en mayor detalle  con propiedad para evitar adelantarnos a hipótesis de trabajo erróneas.
+& No \\
+%\hline
+%¿Presenta dismetría?
+- Nuevamente queremos adelantarnos a hipótesis erróneas a la hora de decidir el método de sensado y procesamiento de las señales.
+La longitud o duración de los movimientos puede usarse como un indicador para nosotros, como también asi los ritmos.
+& Si \\
+%\hline
+%¿Presenta temblores?  - En caso de presentar temblores estos se verán reflejados en las señales y es útil tenerlo en cuenta ya que caracterizará a nuestra señal. & No \\
+%\hline
+%¿Presenta alteraciones en la marcha en instantes previos a la caída?
+- En caso de existir algún impulso inicial que podamos sensar o medir de forma indirecta podemos anticiparnos a la perdida del equilibrio en las señales.
+& Si \\
+%\hline\\
+%¿Cuáles? Si la respuesta fue "No" deje en blanco & Fallas las reacciones de tobillo y cadera \\
+%\hline
+%¿Sufrió alteraciones en la sensibilidad profunda?
+- Existe un trabajo previo en la Universidad de Buenos Aires que usa un método de sensado orientado a la presión de la pisada.
+Esto puede orientarnos en otro sentido en el sensado y estimulación.
+& No  \\
+%\hline
+%Antes de perder el equilibrio, ¿Trastabilla?¿Acelera la marcha?
+-  Al igual que en otras preguntas buscamos obtener información extra para el  procesamiento de las señales y detección del principio de caída.
+Estos fenómenos pueden medirse o detectarse y evidenciarían el inicio de una posible caída.
+& Otro síntoma  \\
+%\hline
+%Si la respuesta fue 'Otro síntoma' ¿Cuál? - En caso contrario deje sin responder & Reacción lenta \\
+%\hline
+%¿Presenta algún tipo de marcha patológica? -la caracterización del caso permite decidir formas y métodos de sensado y procesamiento. & Si  \\
+%\hline
+%¿Cuál? Si la respuesta fue "No" deje la respuesta en blanco & Marcha Atáxica \\
+%\hline
+%¿Existe algún denominador común en las caídas?
+- La presencia de este sería importantisima para  un fenómeno o señal a medir y caracterizar que sería muy útil para la detección del principio de caídas.
+Si hay algo que siempre se repite podríamos enfocarnos en detectar eso.
+& Si \\
+%\hline
+%¿Cuál?
+Si la respuesta fue "No" deje la respuesta en blanco & El denominador es cuando deja de realizar la marcha de manera consciente.
+Por ejemplo, cuando camina y tiene que realizar alguna tarea que implique procesos cognitivo.
+Dual Task  \\
+%\hline
+%¿Se hizo un estudio de evaluación de marcha? - Esta pregunta podría aportar información suplementaria a preguntas anteriores que nos permiten conocer e interiorizarnos en el caso & No  \\
+%\hline
+%¿Se hizo evaluación de riesgo de caídas? - Esta pregunta puede aportar algo de información extra para el conocimiento del caso. & Si  \\
+%\hline
+%¿Hay alguna manera en que trabaje en la reeducación de la paciente?
+-  Quisiéramos conocer un poco mas la situación actual y las actividades que realiza la paciente para su recuperación.
+& Si a través de la reeducación del VOR,  facilitación del equilibrio estático y dinámico, entrenamiento del automatismo de la marcha con diferentes niveles de dificultad.
+\\
+%\hline
+%¿Hay algo mas que desee comentar o expresar?  & Mes a mes se evidencia una mejora, todavía no alcanza para que pueda caminar sin supervisión.  \\
+%\hline
+%\end{tabular}
+%\caption{table}{Answers to survey questions.}
+%\label{tab:alpi_q_table_1}
+%\end{center}
+%\end{table*}
 
 \subsection{Underlying hypothesis}
+\label{sec:hypothesis}
 
-Human balance is composed of a complex interaction of different subsystems, which includes somatosensorial information, vestibular system, visual information, which is later processed in different networks of the Central Nervous System, and actuated by motor pathways at many different scales.
+Human balance is composed of a complex interaction of different subsystems, which includes somatosensorial information, vestibular system and visual information as input sources.
+These are later processed in different networks of the Central Nervous System (CNS), and finally actuated by motor pathways at many different scales~\cite{Donato.etal2016}.
 
-Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey} show the results of the surveys performed on the Patient and their main Rehabilitaion caregivers.
-Using the results from the surveys, we postulate three different systems that could benefit from the introduction of an external signal in the form of biofeedback that can aid in rehabilitation procedures.
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}[!t]{|p{0.45\linewidth} |p{0.45\linewidth} |}
+\hline
+\textbf{Question} & \textbf{Answer} \\
+\hline
+\hline
+Under which situations do you feel you are prone to fall ? & When I am tired, distracted or stressed. \\
+\hline
+What do you feel ?  & I feel that I loss my balance\\
+\hline
+What do you feel before you fall ? & Sometimes I do feel something before.  I realize that I am going to fall, but there isn't anything I can do to avoid it. \\
+\hline
+When do you use the cane ?  & Only when I am out of home.\\
+\hline
+\end{tabular}
+\vspace{10pt}
+\caption{Survey and responses provided by the patient.}
+\label{tab:patientsurvey}
+\end{center}
+\end{table*}
+
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}[!t]{|p{0.45\linewidth} |p{0.45\linewidth} |}
+\hline
+\textbf{Question} & \textbf{Answer} \\
+\hline
+\hline
+Describe the situation when the patient loss her balance & Loss of balance is manifested at the beginning, during the gait cycle or with sudden stops.
+Walking is performed using intense visual compensation.
+When the patient is distracted, or when she stops looking at the floor, or looks sideways, instability increases.
+Gait  is not automated, and demands cognitive resources.
+\\
+\hline
+Is there any significant muscle loss in lower-limbs ? & No \\
+\hline
+Does she presents dysmetria ? & No \\
+\hline
+Does she presents heavy shaking ? & No \\
+\hline
+Does she have any visible reaction before falling?  & She presents dynamic alterations in hip and ankle compensation.\\
+\hline
+Does she have any somatosensorial alteration?  &  No \\
+\hline
+Does she have any proprioceptive alteration?  &  No \\
+\hline
+Is the patient gait normal ?  &  No, the patient presents ataxic gait, likely triggered by slow reaction to perform lower-limb balance correction. \\
+\hline
+Is there any behavioural pattern linked to falling events ? &  Yes, cognitive workload.  Dual tasks situations, when the patient needs to perform something extra while walking. \\
+\hline
+Describe current treatment.
+& The patient is currently working on rehabilitation exercises to retrain her Vestibulo-Ocular Reflex (VOR), to improve her static and dynamic balance, and improve her locomotor automatism.
+She is improving on a montly basis, but still she has not reached the level to walk autonomy without any aid.
+\\
+\hline
+\end{tabular}
+\vspace{10pt}
+\caption{Survey and responses provided by his main professional rehabilitation caregiver.}
+\label{tab:caregiverssurvey}
+\end{center}
+\end{table*}
+
+We perform a series of surveys and interviews with the patient and their caregivers.  Main results are summarized in 
+Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey}.
+Based on the clinical history, the results from the surveys and interviews, we postulate three different potential clinical situations that could use the external signal in the form of biofeedback and could potentially aid in rehabilitation procedures.
+The first (i) is a potential problem in the integration of vestibular information while walking, the second (ii) is bradykinesia where the required processing speed to effectively adjust the lower limb to keep the center of mass inside the base support is not achieved.
+Finally, the (iii) hypothesis is an ataxic gait, where non-automated gait produces an increase in the likelihood of failing.
 
@@
 
-\begin{itemize}
-\item Vestibular information on fusion of vestibular information
-\item Bradykinesia: the processing speed required to effectively perform the processing and actuation is not enough.
-\item Unusual gait
-\end{itemize}
-
-Based on the surveys and the information provided by caregivers there seems not to be any somatosensorial deficit\cite{cite}.
+%\begin{itemize}
+%\item Vestibular information or fusion of vestibular information
+%\item Bradykinesia: the processing speed required to effectively perform the processing and actuation is not enough.
+%\item Ataxic gait: the movement is not normally regulated.
+%\end{itemize}
+%
 
 \subsection{Robotic Device Vest}
-Description of the system.
-How does it work, how is the detection of IMU working
-Internet of Robotic Things.
-Arduino
+\label{sec:vest}
 
-\textbf{Why only vibrotactile stimulation and not auditory stimulation}
+The vest system prototype is based on Internet of Robot Thing (IoRT) technology~\cite{Simoens.etal2018,Domingo.etal2012}.
+The controller is an Arduino UNO (Arduino LLC, Italy) board coupled with ESP8266 shield (WeMos, United Kingdom).
+The system is powered by a commercial power bank with Li-Po 18650 cells (Ipower, United States), an inertial measurement unit Inertial Measurement Unit (IMU) MPU 6050 (OEM ITG/MPU6050) and a FA-12350 DC motor scavenged from old compact discs which provide the vibrotactile feedback.
+The IMU uses the accelerometer and gyroscope data to get 3-dimensional angular acceleration and measure pitch roll and yaw angles.
+These angles are calculated from a set of transforming equations and processed with a complementary filter which relies 80\% in gyroscope data and 20\% in accelerometer data~\cite{Fetick.2022}.
+These values are transmitted by telemetry in real-time as UDP packets for off-board register, processing and further analysis.
+Data recovered by the device is sampled at 1000 Hz.
+
+The smart-vest prototype can be seen in Figure~\ref{fig:smart-vest} ......
+
+%\textbf{Why only vibrotactile stimulation and not auditory stimulation}
 
 \subsection{Experimental Design}
+\label{sec:experimental}
 
-Three experiments were designed in order to test each one of the hypothesis.  All the experiments were approved by the ITBA University ethical committee.  Participants were recruited voluntarily.
+Three experiments are designed in order to assess each one of the potential clinical causes, and to derive for each one of them a stimulation strategy.
+Participants are recruited voluntarily and the experiment is conducted anonymously in accordance with the declaration of Helsinki published by the World Health Organization.
+No monetary compensation is handed out and all participants agree and sign a written informed consent.
+This study is approved by the Departamento de Investigación y Doctorado, Instituto Tecnológico de Buenos Aires (ITBA).
+All the participants wear the smart-vest with an elastic band pressed tightly towards the chest, tied in no-restrictive manner, holding the sensor firmly.
 
@@
 
-\subsubsection{Vestibular Feedback}
+\subsubsection{Vestibular Information Integration}
 
-The underlying idea is that signals from IMU can be feed back to the patient by vibrotactile stimulation on their belly.
-The hypothesis is that if there is a vestibular problem that forbids the patient to receive or evaluate the vestibular information appropriately, this external signal can be available for the patient to integrate it into the dynamic balance integration.
+This experiment aims to study the falling process.
+Participants are told to lean forward until they couldn't maintain balance anymore and let themselves fall into a mattress.
+This experiment is used to determine a threshold for the data that can help to identify the breakpoint conditions based on the IMU information where each subject falls.
 
-In order to test it, 5 healthy participants are going to be recruited to simulate falling breakpoint conditions on the IMU information.
-Participants wear the vest and perform a forward walking exercise with the upper-trunk leaned forward at different angles progresively until they can no longer cope with the unbalance situation without stepping forward.
+In order to test it, 5 healthy participants are recruited to perform 10 runs of falling situations  Participants wearing the vest  perform a one-step forward walking exercise with the upper-trunk leaned forward at different angles progressively until they can no longer cope with the unbalance situation and fall to the mattress.
 
-Afterward, the experiment will be repeated with the 5 participants activating the vibrotactile stimulation which will map progressively the inclination angle.
-Hence it will provide an extra signal that can give a accurate information in relation to the stability of the upper-trunk in relation to the walking gait.
+\subsubsection{Ataxic Gait}
 
-\subsubsection{Bradykinesia: Fall prediction due to insufficient speed of step}
+This experiment has the purpose of analyzing and studying gait's behavior.
+In order to accomplish this,  5 participants are instructed to perform 10 sessions of walking in a straight line across ten meters, performing Ten-Meter Walking (10MWT) assesment~\cite{Olmos.etal2008}.
+We collected and analyzed pitch, roll and yaw values as well as angular acceleration changes registered by the IMU gyroscope.
+In this study our goal is to be able to process and identify gait abnormalities as well as all steps occurring and any fall that might develop.
 
-All the IMU information represent a multichannel time series.  Hence, it can be used to predict a falling situation.
+\subsubsection{Bradykinesia}
 
-In this case, 5 healthy participants perform 20 controlled falls over gym mats.
+This experiment involves the coupling of the other two.
+Five participants are instructed to perform 10 runs of a ten-meter walking procedure, followed by a falling into a mattress.
+The purpose of this experiment is obtain a multichannel time series of the whole sequence, including the walk and the falling action.
 
-(3) Ver en base a la encuesta como se da la situación de caída más común que Paula relata, en base a lo que ella manifiesta.
+%(3) Ver en base a la encuesta como se da la situación de caída más común que Paula relata, en base a lo que ella manifiesta.
 Entonces lo que hacemos es tomamos 5 sujetos y los hacemos caer 5 veces cada uno sobre la colchoneta (o 10 o 20 x sujeto, lo que más puedas).
@@
 
-10 participants simulating falls.
-
-\subsubsection{Gait Pacemaker}
-
-This is a gait pacemaker coupled with a podometer.  It has been showed that gait synchronization with music achieved better effect \cite{Roerdink.etal2007}.
-
-(4) En este caso, lo que hacemos es armar un gráfico de gait y lo que hace el dispositivo es detectar un punto en el ciclo y vibrar de forma recurrente, como un marca paso, basado en un podómetro.
+%(4) En este caso, lo que hacemos es armar un gráfico de gait y lo que hace el dispositivo es detectar un punto en el ciclo y vibrar de forma recurrente, como un marca paso, basado en un podómetro.
 En este caso, tomás 5 personas las hacés caminar, determinás cómo son esas curvas y accionás el motor siempre en el mismo momento.
@@
 
-%\subsection{Abbreviations and Acronyms}\label{AA}
-%Define abbreviations and acronyms the first time they are used in the text, 
-%even after they have been defined in the abstract. Abbreviations such as 
-%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-%abbreviations in the title or heads unless they are unavoidable.
-%
-%\subsection{Units}
-%\begin{itemize}
-%\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-%\end{itemize}
-%
-%\subsection{Equations}
-%Number equations consecutively. To make your 
-%equations more compact, you may use the solidus (~/~), the exp function, or 
-%appropriate exponents. Italicize Roman symbols for quantities and variables, 
-%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-%sign. Punctuate equations with commas or periods when they are part of a 
-%sentence, as in:
-%\begin{equation}
-%a+b=\gamma\label{eq}
-%\end{equation}
-%
-%Be sure that the 
-%symbols in your equation have been defined before or immediately following 
-%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-%
-%\subsection{\LaTeX-Specific Advice}
-%
-%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-%to combine sections, add equations, or change the order of figures or
-%citations without having to go through the file line by line.
-%
-%Please don't use the \verb|{eqnarray}| equation environment. Use
-%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-%environment leaves unsightly spaces around relation symbols.
-%
-%Please note that the \verb|{subequations}| environment in {\LaTeX}
-%will increment the main equation counter even when there are no
-%equation numbers displayed. If you forget that, you might write an
-%article in which the equation numbers skip from (17) to (20), causing
-%the copy editors to wonder if you've discovered a new method of
-%counting.
-%
-%{\BibTeX} does not work by magic. It doesn't get the bibliographic
-%data from thin air but from .bib files. If you use {\BibTeX} to produce a
-%bibliography you must send the .bib files. 
-%
-%{\LaTeX} can't read your mind. If you assign the same label to a
-%subsubsection and a table, you might find that Table I has been cross
-%referenced as Table IV-B3. 
-%
-%{\LaTeX} does not have precognitive abilities. If you put a
-%\verb|\label| command before the command that updates the counter it's
-%supposed to be using, the label will pick up the last counter to be
-%cross referenced instead. In particular, a \verb|\label| command
-%should not go before the caption of a figure or a table.
-%
-%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-%will not stop equation numbers inside \verb|{array}| (there won't be
-%any anyway) and it might stop a wanted equation number in the
-%surrounding equation.
-%
-%\subsection{Some Common Mistakes}\label{SCM}
-%\begin{itemize}
-%\item The word ``data'' is plural, not singular.
-%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-%\item Do not confuse ``imply'' and ``infer''.
-%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-%\end{itemize}
-%An excellent style manual for science writers is \cite{b7}.
-%
-%\subsection{Authors and Affiliations}
-%\textbf{The class file is designed for, but not limited to, six authors.} A 
-%minimum of one author is required for all conference articles. Author names 
-%should be listed starting from left to right and then moving down to the 
-%next line. This is the author sequence that will be used in future citations 
-%and by indexing services. Names should not be listed in columns nor group by 
-%affiliation. Please keep your affiliations as succinct as possible (for 
-%example, do not differentiate among departments of the same organization).
-%
-%\subsection{Identify the Headings}
-%Headings, or heads, are organizational devices that guide the reader through 
-%your paper. There are two types: component heads and text heads.
-%
-%Component heads identify the different components of your paper and are not 
-%topically subordinate to each other. Examples include Acknowledgments and 
-%References and, for these, the correct style to use is ``Heading 5''. Use 
-%``figure caption'' for your Figure captions, and ``table head'' for your 
-%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-%style (in this case, italic) in addition to the style provided by the drop 
-%down menu to differentiate the head from the text.
-%
-%Text heads organize the topics on a relational, hierarchical basis. For 
-%example, the paper title is the primary text head because all subsequent 
-%material relates and elaborates on this one topic. If there are two or more 
-%sub-topics, the next level head (uppercase Roman numerals) should be used 
-%and, conversely, if there are not at least two sub-topics, then no subheads 
-%should be introduced.
-%
-%\subsection{Figures and Tables}
-%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-%bottom of columns. Avoid placing them in the middle of columns. Large 
-%figures and tables may span across both columns. Figure captions should be 
-%below the figures; table heads should appear above the tables. Insert 
-%figures and tables after they are cited in the text. Use the abbreviation 
-%``Fig.~\ref{fig}'', even at the beginning of a sentence.
-%
-%\begin{table}[htbp]
-%\caption{Table Type Styles}
-%\begin{center}
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-%\cline{2-4} 
-%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-%\hline
-%copy& More table copy$^{\mathrm{a}}$& &  \\
-%\hline
-%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-%\end{tabular}
-%\label{tab1}
-%\end{center}
-%\end{table}
-%
-%\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
-%\caption{Example of a figure caption.}
-%\label{fig}
-%\end{figure}
-%
-%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-%rather than symbols or abbreviations when writing Figure axis labels to 
-%avoid confusing the reader. As an example, write the quantity 
-%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-%units in the label, present them within parentheses. Do not label axes only 
-%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-%quantities and units. For example, write ``Temperature (K)'', not 
-%``Temperature/K''.
-
 \section*{Results}
 
-(1) Se muestran entonces esos dos gráficos promediados de cada uno de los 5 sujetos (10 series, 5 sin el motor, 5 con el motor).
+Preliminary results show that ........
 
-(2) Se muestra los gráficos de las series de tiempo offline de los datos analizados y como el sistema online de predicción acierta justamente en anticipar la caída.
+%(1) Se muestran entonces esos dos gráficos promediados de cada uno de los 5 sujetos (10 series, 5 sin el motor, 5 con el motor).
+%
+%
+%(2) Se muestra los gráficos de las series de tiempo offline de los datos analizados y como el sistema online de predicción acierta justamente en anticipar la caída.
 (Esto es probablmente desde software lo más complejo).
-
-(3) Este caso probablemente sea el que requiera más experimentación sobre Paula en sí misma.
+%
+%(3) Este caso probablemente sea el que requiera más experimentación sobre Paula en sí misma.
 La idea acá es tener los gráficos promediados de GAIT, que son todos cíclicos, de dos de las variables cualquiera del IMU que formen un ciclo, y ver que hay un patrón común que se da más o menos para las personas healthy.
@@
 
+The information provided from all the experiments allow us to implement three different VF strategies:  The first is an \textbf{Artificial Vestibular Feedback}, which provides information as a feedback for vestibular information integration process.
+This is implemented as a frequency-increasing VF signal that represents a distance from the breaking condition position where the fall is inevitable.
+The purpose is to provide the patient with a continuous sensation that modulates the risk of falling.
+
+The second strategy is the implementation of \textbf{Gait Pacemaker}.
+The obtained data from the analysis of the ataxic gait is used to implement a podometer.
+It has been showed that gait synchronization with music increase gait performance~\cite{Roerdink.etal2007} and synchronized gait trainer achieved positive results on patient~\cite{Blicher.etal2009}.
+Hence, the aim of this stimulation approach is to drive the keep the patient as close as possible to a normal and safe gait.
+
+The final stimulation approach deals with the Bradykinesia condition, and aims to have a \textbf{Risk-Predictor}~\cite{Rahman.etal2022,Ali.etal2022}.
+The IMU data  represents a multichannel time series.
+Hence, it can be used to predict a risk of falling, ahead of its occurrence, by implement a machine-learning predictor, based on the analysis of the time-series data.
+The rationale is to counter the slowness of the response by predicting ahead of its occurrence, a high risk of falling, and providing the VF stimulation to force a change in the gait pattern.
+
+%Hence, the signals  IMU can be feed back to the patient by vibrotactile stimulation on their belly.
+This will be impemented, first, in a binary way.
+The hypothesis is that if there is a vestibular problem that forbids the patient to receive or evaluate the vestibular information appropriately, this external signal can be available for the patient to integrate it into the dynamic balance system.
+
+%Afterward, the experiment will be repeated with the 5 participants activating the vibrotactile stimulation which will map progressively the inclination angle.
+Hence it will provide an extra signal that can give a accurate information in relation to the stability of the upper-trunk in relation to the walking gait.
+
 \section*{Conclusion}
+Overall, this device allow to implement a testbed that can be iteratively extended to obtain experimental data and to implement biofeedback strategies which could potentially lead to an increase in the effectiveness of different rehabilitation procedures~\cite{Bowman2021}.
 
-This device used as a testbed can be extended easily to provide biofeedback which also aim to increase the effectiveness of rehabilitation procedures~\cite{Bowman2021}.
-
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 

### 2022-09-17 iros.tex
Update fixing some errores of the manuscript.

@@
 Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning have appeared as an alternative treatment to increase neuralplasticity.
-These are in the form of Wearable devices-based biofeedback rehabilitation (WDBR)~\cite{Peake.etal2018} or more advanced robotic rehabilitation gait devices~\cite{Zhao.etal2022,Peshkin.etal2005,Tong.etal2006}.
+These are in the form of Wearable devices-based biofeedback rehabilitation (WDBR)~\cite{Peake.etal2018} or robotic rehabilitation gait devices~\cite{Zhao.etal2022,Peshkin.etal2005,Tong.etal2006}.
 
@@
 
-After 24 months since event, the patient, was discharged from hospital and only maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related with dynamic balance problems while walking.
+After 24 months since event, the patient, was discharged from hospital and maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related to dynamic balance problems while walking.
 The patient achieved satisfactory index scores in static balance tests and is able to perform static hip-balance and ankle-balance.
@@
 
-However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or while walking concentration fades, she is unable to keep up with the pace of the gait and the risk of fall increases.
+However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or when concentration fades while walking, she is unable to keep up with the pace of the gait and the risk of fall increases.
 Nowadays, the patient walks freely unaided at home but requires a Canadian cane otherwise.
@@
 The first (i) is a potential problem in the integration of vestibular information while walking, the second (ii) is bradykinesia where the required processing speed to effectively adjust the lower limb to keep the center of mass inside the base support is not achieved.
-Finally, the (iii) hypothesis is an ataxic gait, where non-automated gait produces an increase in the likelihood of failing.
+Finally, the third (iii) hypothesis is an ataxic gait, where non-automated gait produces an increase in the likelihood of failing.
 
@@
 The controller is an Arduino UNO (Arduino LLC, Italy) board coupled with ESP8266 shield (WeMos, United Kingdom).
-The system is powered by a commercial power bank with Li-Po 18650 cells (Ipower, United States), an inertial measurement unit Inertial Measurement Unit (IMU) MPU 6050 (OEM ITG/MPU6050) and a FA-12350 DC motor scavenged from old compact discs which provide the vibrotactile feedback.
+The system is powered by a commercial power bank with Li-Po 18650 cells (Ipower, United States).
+It also contains an Inertial Measurement Unit (IMU) MPU 6050 (OEM ITG/MPU6050) and a FA-12350 DC motor scavenged from old compact discs which provide the vibrotactile feedback.
 The IMU uses the accelerometer and gyroscope data to get 3-dimensional angular acceleration and measure pitch roll and yaw angles.
@@
 It has been showed that gait synchronization with music increase gait performance~\cite{Roerdink.etal2007} and synchronized gait trainer achieved positive results on patient~\cite{Blicher.etal2009}.
-Hence, the aim of this stimulation approach is to drive the keep the patient as close as possible to a normal and safe gait.
+Hence, the aim of this stimulation approach is to keep the patient as close as possible to a normal and safe gait.
 
-The final stimulation approach deals with the Bradykinesia condition, and aims to have a \textbf{Risk-Predictor}~\cite{Rahman.etal2022,Ali.etal2022}.
+The final stimulation scheme deals with the Bradykinesia condition, and aims to have a \textbf{Risk-Predictor}~\cite{Rahman.etal2022,Ali.etal2022}.
 The IMU data  represents a multichannel time series.
-Hence, it can be used to predict a risk of falling, ahead of its occurrence, by implement a machine-learning predictor, based on the analysis of the time-series data.
-The rationale is to counter the slowness of the response by predicting ahead of its occurrence, a high risk of falling, and providing the VF stimulation to force a change in the gait pattern.
+Hence, it can be used to predict a risk of falling, ahead of its occurrence, by implement a machine-learning predictor based on the analysis of the time-series data.
+The rationale is to counter the slowness of the response by predicting the falling situation ahead of its occurrence and providing the VF stimulation to force a change in the risky gait pattern.
 
@@
 \section*{Conclusion}
-Overall, this device allow to implement a testbed that can be iteratively extended to obtain experimental data and to implement biofeedback strategies which could potentially lead to an increase in the effectiveness of different rehabilitation procedures~\cite{Bowman2021}.
+Overall, this devices allows to implement a testbed that can be iteratively extended to obtain experimental data and to implement biofeedback strategies which could potentially lead to an increase in the effectiveness of different rehabilitation procedures~\cite{Bowman2021}.
 

### 2022-09-18 iros.tex
Base version almost ready.

@@
 
-\begin{abstract}
-Stroke is a medical condition that can affect motor function, particularly dynamic balance.
+%\begin{abstract}
+%Stroke is a medical condition that can affect motor function, particularly dynamic balance.
 Biofeedback can aid in rehabilitaiton procedures which help patients to regain lost motor activity and recover functionality.
@@
 Information provided by principal caregivers, family, patient in the form of surveys and interview, is used to derive potential clinical causal hypothesis and these are used to drive the experimentation paradigm, and the robotic smart-vest to aid in the whole procedure...
-\end{abstract}
+%\end{abstract}
 
@@
 These procedures are aimed to relearn movements that can trigger new neural pathway generation which reroute, or even completely replace, those pathways that were damaged by the stroke.
-Neurorehabilitation procedures are performed by a group of interdisciplinary caregivers and technicians.
-Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning have appeared as an alternative treatment to increase neuralplasticity.
+Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning have appeared as a complementary treatment to increase neuralplasticity.
 These are in the form of Wearable devices-based biofeedback rehabilitation (WDBR)~\cite{Peake.etal2018} or robotic rehabilitation gait devices~\cite{Zhao.etal2022,Peshkin.etal2005,Tong.etal2006}.
+
+%Neurorehabilitation procedures are performed by a group of interdisciplinary caregivers and technicians.
 
@@
 
-Section \ref{sec:case-study} presents the case study.
+%Section \ref{sec:case-study} presents the case study.
 Next section \ref{sec:hypothesis} summarize the results of the interviews and surveys performed by the patient, their family and professional caregivers, presenting the underlying clinical causal hypothesis.
@@
 Walking is performed using intense visual compensation.
-When the patient is distracted, or when she stops looking at the floor, or looks sideways, instability increases.
-Gait  is not automated, and demands cognitive resources.
+Instability increase when the patient is distracted, when she stops looking at the floor, or when she looks sideways.
+Her gait is not automated, and demands cognitive resources.
 \\
 \hline
-Is there any significant muscle loss in lower-limbs ? & No \\
+Is there any significant muscle loss in lower-limbs ? & No\\
 \hline
-Does she presents dysmetria ? & No \\
-\hline
-Does she presents heavy shaking ? & No \\
+Does she presents any of the following dysmetria / heavy shaking / somatosensorial alterations / proprioceptive alterations ? & No \\
 \hline
 Does she have any visible reaction before falling?  & She presents dynamic alterations in hip and ankle compensation.\\
-\hline
-Does she have any somatosensorial alteration?  &  No \\
-\hline
-Does she have any proprioceptive alteration?  &  No \\
 \hline
@@
 Data recovered by the device is sampled at 1000 Hz.
+The smart-vest prototype can be seen in Figure~\ref{fig:smart-vest}.
+It is based on a safety vest, complemented with velcro pockets.
 
-The smart-vest prototype can be seen in Figure~\ref{fig:smart-vest} ......
+\begin{figure}[h!]
+\centering
+\includegraphics[width=8cm]{equilivest.jpg}
+\caption{Front view and back view of the Equilivest prototype.
+The vest is based on a safety vest, with additional velcro pockets.
+The battery is located on the back, while the vibrotactile motor is located in the belly~\cite{Brandebusemeyer.etal2021}.
+The IMU sensor is pressed against the chest by the use of a flexible elastic band.
+}
+\label{fig:smart-vest}
+\end{figure}
 
@@
 Preliminary results show that ........
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=8cm]{gait.png}
+\caption{fdsfsdfdsfdsf }
+\label{fig:smart-vest}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=8cm]{gait.png}
+\caption{dfsfsdfs }
+\label{fig:smart-vest}
+\end{figure}
 

### 2022-09-18 iros.tex
Good candidate version.

@@
 Disabilities related to stroke can affect motor pathways, and may lead to several motor function disorders.
-One important aspect of motor function is balance which is the ability to control the center of mass of the body inside the base support provided by the lower limb~\cite{Bowman2021}.
+One important aspect of motor function is balance which is the ability to control the body's center of mass inside the base support provided by the lower limb~\cite{Bowman2021}.
 Stroke can affect dynamic balance as well,  which is manifested while walking, impairing autonomy and independence, important factors in Activities of Daily Living (ADL) particularly for young patients~\cite{Afrasiabifar.etal2020,Donato.etal2016}.
@@
 These procedures are aimed to relearn movements that can trigger new neural pathway generation which reroute, or even completely replace, those pathways that were damaged by the stroke.
-Recently, biofeedback techniques, aiming at providing extra information to the patient that can be used to aid in the relearning have appeared as a complementary treatment to increase neuralplasticity.
+Recently, biofeedback techniques aiming to provide extra information to the patient to aid in the relearning, have appeared as a complementary treatment to increase neuralplasticity.
 These are in the form of Wearable devices-based biofeedback rehabilitation (WDBR)~\cite{Peake.etal2018} or robotic rehabilitation gait devices~\cite{Zhao.etal2022,Peshkin.etal2005,Tong.etal2006}.
@@
 \end{tabular}
-\vspace{10pt}
-\caption{Survey and responses provided by the patient.}
+\vspace{2pt}
+\caption{Survey and responses provided by the patient and family.}
 \label{tab:patientsurvey}
@@
 \end{tabular}
-\vspace{10pt}
-\caption{Survey and responses provided by his main professional rehabilitation caregiver.}
+\vspace{2pt}
+\caption{Survey and responses provided by his main patient's rehabilitation caregiver.}
 \label{tab:caregiverssurvey}
@@
 Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey}.
-Based on the clinical history, the results from the surveys and interviews, we postulate three different potential clinical situations that could use the external signal in the form of biofeedback and could potentially aid in rehabilitation procedures.
+Based on the clinical history, results from surveys and interviews, we postulate three different potential clinical situations that could use the external biofeedback signal and could potentially aid in rehabilitation procedures.
 The first (i) is a potential problem in the integration of vestibular information while walking, the second (ii) is bradykinesia where the required processing speed to effectively adjust the lower limb to keep the center of mass inside the base support is not achieved.
@@
 It also contains an Inertial Measurement Unit (IMU) MPU 6050 (OEM ITG/MPU6050) and a FA-12350 DC motor scavenged from old compact discs which provide the vibrotactile feedback.
-The IMU uses the accelerometer and gyroscope data to get 3-dimensional angular acceleration and measure pitch roll and yaw angles.
-These angles are calculated from a set of transforming equations and processed with a complementary filter which relies 80\% in gyroscope data and 20\% in accelerometer data~\cite{Fetick.2022}.
+The IMU provides accelerometer and gyroscope data to get a 3-dimensional angular acceleration vector and a linear acceleration vector.
+Pitch, Roll and Yaw angles are calculated from a set of transforming equations and processed with a complementary filter which relies 80\% in gyroscope data and 20\% in accelerometer data~\cite{Fetick.2022}.
 These values are transmitted by telemetry in real-time as UDP packets for off-board register, processing and further analysis.
@@
 \includegraphics[width=8cm]{equilivest.jpg}
-\caption{Front view and back view of the Equilivest prototype.
+\caption{Front and back view of the Equilivest prototype.
 The vest is based on a safety vest, with additional velcro pockets.
-The battery is located on the back, while the vibrotactile motor is located in the belly~\cite{Brandebusemeyer.etal2021}.
+The battery is located on the back, while the vibrotactile motor is located on the belly~\cite{Brandebusemeyer.etal2021}.
 The IMU sensor is pressed against the chest by the use of a flexible elastic band.
@@
 
-\section*{Results}
+\section*{Results and Discussion}
 
-Preliminary results show that ........
+Preliminary results show that for the (1) experiment, the pitch,roll, yaw angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1).
+Results from experiment number (2), show that the gait cycle are clearly visible from the raw and pitch data.
 
@@
 \centering
-\includegraphics[width=8cm]{gait.png}
-\caption{fdsfsdfdsfdsf }
-\label{fig:smart-vest}
+\includegraphics[width=8cm]{vestibular.png}
+\caption{Pitch value in degrees showing the progressive increase as participants leaned forward crossing the instability condition (1).  Time is in milliseconds. }
+\label{fig:vestibular}
 \end{figure}
@@
 \includegraphics[width=8cm]{gait.png}
-\caption{dfsfsdfs }
-\label{fig:smart-vest}
+\caption{Angular acceleration for the X and Y axis showing 7 steps of the 10MWT assessment.   }
+\label{fig:gait}
 \end{figure}
@@
 A partir de que vemos si cambia hay que ver donde cambia y en ese punto meter el pacemaker.
-
-\section*{Discussion}
 

### 2022-09-18 iros.tex
Fix some issues.

@@
 \hline
-Is there any behavioural pattern linked to falling events ? &  Yes, cognitive workload.  Dual tasks situations, when the patient needs to perform something extra while walking. \\
+Is there any behavioral pattern linked to falling events ? &  Yes, cognitive workload.  Dual tasks situations, when the patient needs to perform something extra while walking. \\
 \hline
@@
 & The patient is currently working on rehabilitation exercises to retrain her Vestibulo-Ocular Reflex (VOR), to improve her static and dynamic balance, and improve her locomotor automatism.
-She is improving on a montly basis, but still she has not reached the level to walk autonomy without any aid.
+She is improving on a monthly basis, but still she has not reached the level to walk autonomy without any aid.
 \\
@@
 The IMU provides accelerometer and gyroscope data to get a 3-dimensional angular acceleration vector and a linear acceleration vector.
-Pitch, Roll and Yaw angles are calculated from a set of transforming equations and processed with a complementary filter which relies 80\% in gyroscope data and 20\% in accelerometer data~\cite{Fetick.2022}.
+Pitch, Roll and Yaw angles are calculated from a set of transforming equations and processed with a complementary filter which relies $0.98$ in gyroscope data and $0.02$ in accelerometer data~\cite{Fetick.2022}.
 These values are transmitted by telemetry in real-time as UDP packets for off-board register, processing and further analysis.
-Data recovered by the device is sampled at 1000 Hz.
+Data recovered by the device is sampled at 100 Hz.
 The smart-vest prototype can be seen in Figure~\ref{fig:smart-vest}.
-It is based on a safety vest, complemented with velcro pockets.
+It is based on a safety vest, complemented with Velcro pockets.
 
@@
 \centering
-\includegraphics[width=8cm]{equilivest.jpg}
+\includegraphics[width=8cm]{equilivest.png}
 \caption{Front and back view of the Equilivest prototype.
@@
 
-Preliminary results show that for the (1) experiment, the pitch,roll, yaw angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1).
-Results from experiment number (2), show that the gait cycle are clearly visible from the raw and pitch data.
+Preliminary results show that for the (1) experiment (Figure \ref{fig:vestibular}), the pitch,roll, yaw angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1).
+Results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle are clearly visible from raw acceleration data.
 
@@
 \includegraphics[width=8cm]{gait.png}
-\caption{Angular acceleration for the X and Y axis showing 7 steps of the 10MWT assessment.   }
+\caption{Angular acceleration for the X and Y axis showing 7 steps of the 10MWT assessment.  Time is in milliseconds. }
 \label{fig:gait}
@@
 The IMU data  represents a multichannel time series.
-Hence, it can be used to predict a risk of falling, ahead of its occurrence, by implement a machine-learning predictor based on the analysis of the time-series data.
+Hence, it can be used to predict a risk of falling, ahead of its occurrence, by building a machine-learning predictor based on the analysis of the time-series data.
 The rationale is to counter the slowness of the response by predicting the falling situation ahead of its occurrence and providing the VF stimulation to force a change in the risky gait pattern.

### 2022-09-19 iros.tex
Almost ready.

@@
                     Buenos Aires, Argentina
-        {\tt\small juanmiguelsantos@gmail.com}}%
+        {\tt\small juan.santos@unahur.edu.ar}}%
 %\thanks{*This work was not supported by any organization}% <-this % stops a space}
@@
 Patient was in coma for around 2 months, and after that unable to walk, move, talk or swallow.
-After two years of intensive rehabilitation, Patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.
+After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.
 
@@
 The patient achieved satisfactory index scores in static balance tests and is able to perform static hip-balance and ankle-balance.
-She has recovered muscle in her legs and can perform lower-limb exercises.
+She has recovered muscle force in her legs and can perform lower-limb exercises.
 Her vision is normal.
@@
 \vspace{2pt}
-\caption{Survey and responses provided by the patient and family.}
+\caption{Survey and responses provided by the patient.}
 \label{tab:patientsurvey}
@@
 \hline
-Is there any significant muscle loss in lower-limbs ? & No\\
-\hline
-Does she presents any of the following dysmetria / heavy shaking / somatosensorial alterations / proprioceptive alterations ? & No \\
+Does she presents any of the following muscular dystrophy in lower-limbs / dysmetria / heavy shaking / somatosensorial alterations / proprioceptive alterations ? & No \\
 \hline
@@
 Tables ~\ref{tab:patientsurvey} and \ref{tab:caregiverssurvey}.
-Based on the clinical history, results from surveys and interviews, we postulate three different potential clinical situations that could use the external biofeedback signal and could potentially aid in rehabilitation procedures.
+Based on these results and patient's clinical history, we postulate three different potential clinical situations that could use the external biofeedback signal eventually aiding in rehabilitation procedures.
 The first (i) is a potential problem in the integration of vestibular information while walking, the second (ii) is bradykinesia where the required processing speed to effectively adjust the lower limb to keep the center of mass inside the base support is not achieved.
@@
 \includegraphics[width=8cm]{equilivest.png}
-\caption{Front and back view of the Equilivest prototype.
+\caption{Front and back views of the Equilivest prototype.
 The vest is based on a safety vest, with additional velcro pockets.
@@
 
-Preliminary results show that for the (1) experiment (Figure \ref{fig:vestibular}), the pitch,roll, yaw angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1).
-Results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle are clearly visible from raw acceleration data.
+Preliminary results show that for the (1) experiment, on Figure \ref{fig:vestibular}), the value of pitch angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1*).
+Results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle is clearly visible from raw acceleration data.
 
@@
 \includegraphics[width=8cm]{vestibular.png}
-\caption{Pitch value in degrees showing the progressive increase as participants leaned forward crossing the instability condition (1).  Time is in milliseconds. }
+\caption{Pitch value in degrees and angular acceleration around X axis showing the progressive increase as participants leaned forward crossing the instability condition (1).
+Time is in milliseconds.
+}
 \label{fig:vestibular}
@@
 \includegraphics[width=8cm]{gait.png}
-\caption{Angular acceleration for the X and Y axis showing 7 steps of the 10MWT assessment.  Time is in milliseconds. }
+\caption{Angular acceleration for the X and Z axis showing 7 steps of the 10MWT assessment.  Time is in milliseconds. }
 \label{fig:gait}
@@
 The information provided from all the experiments allow us to implement three different VF strategies:  The first is an \textbf{Artificial Vestibular Feedback}, which provides information as a feedback for vestibular information integration process.
-This is implemented as a frequency-increasing VF signal that represents a distance from the breaking condition position where the fall is inevitable.
+This is implemented as a frequency-increasing VF signal that increases as long as the distance from the breaking condition position where the fall is inevitable decreases.
 The purpose is to provide the patient with a continuous sensation that modulates the risk of falling.
 
-The second strategy is the implementation of \textbf{Gait Pacemaker}.
+The second strategy, independent of the first one, is the implementation of \textbf{Gait Pacemaker}.
 The obtained data from the analysis of the ataxic gait is used to implement a podometer.
@@
 \section*{Conclusion}
-Overall, this devices allows to implement a testbed that can be iteratively extended to obtain experimental data and to implement biofeedback strategies which could potentially lead to an increase in the effectiveness of different rehabilitation procedures~\cite{Bowman2021}.
+Overall, we aim for \textit{Equilivest} to serve as a testbed that can be iteratively extended to obtain experimental data and to implement biofeedback strategies~\cite{Bowman2021}.
 

### 2022-09-20 iros.tex
Submitted version.

@@
 Franco Paviotti$^{1}$, Esteban Buniak$^{2}$, Rodrigo Ramele$^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
-\thanks{$^{1}$F. Paviotti is with Bioengineering, Instituto Tecnológico de Buenos Aires
+\thanks{$^{1}$F. Paviotti is with Bioengineering, Instituto Tecnológico de Buenos Aires (ITBA)
                     Buenos Aires, Argentina
         {\tt\small fpaviotti@itba.edu.ar}}%
-\thanks{$^{2}$E.Buniak is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires
+\thanks{$^{2}$E.Buniak is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires (ITBA)
                     Buenos Aires, Argentina
         {\tt\small ebuniak@itba.edu.ar}}%
-\thanks{$^{3}$R.Ramele is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires
+\thanks{$^{3}$R.Ramele is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires (ITBA)
                     Buenos Aires, Argentina
@@
 \begin{IEEEkeywords}
-Stroke, Balance, Rehabilitation, Biofeedback, Vibrotactile
+Stroke, Dynamic Balance, Neurorehabilitation, Biofeedback, Vibrotactile
 \end{IEEEkeywords}
@@
 
-Patient is a 31 years old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.
+Patient is a 31 years-old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.
 The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.
@@
 
-Preliminary results show that for the (1) experiment, on Figure \ref{fig:vestibular}), the value of pitch angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1*).
-Results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle is clearly visible from raw acceleration data.
+Preliminary results show that for the first (1) experiment, on Figure \ref{fig:vestibular}, the pitch angle can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1*).
+On the other hand, results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle is clearly visible from raw acceleration data.
 

### 2022-09-29 iros.tex
Fixed wrongfully data about the patient.

@@
 
-Patient is a 31 years-old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.
+Patient is a 36 years-old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.
 The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.
-Patient was in coma for around 2 months, and after that unable to walk, move, talk or swallow.
+Patient was in induced coma for around 1 month, and after that unable to walk, move, talk or swallow.
 After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.
 
-After 24 months since event, the patient, was discharged from hospital and maintained a 3 times per week rehabilitation treatment, focusing on a remaining affection related to dynamic balance problems while walking.
+After 7 months since event, the patient, was discharged from hospital and maintained a daily rehabilitation treatment, focusing on a remaining affection related to dynamic balance problems while walking.
 The patient achieved satisfactory index scores in static balance tests and is able to perform static hip-balance and ankle-balance.
@@
 However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or when concentration fades while walking, she is unable to keep up with the pace of the gait and the risk of fall increases.
-Nowadays, the patient walks freely unaided at home but requires a Canadian cane otherwise.
+Nowadays, the patient walks freely unaided at home but requires a Canadian cane otherwise and constant supervision.
 

### 2022-10-10 review/iros_original.tex
Submitted after review version.@

--- 2022-09-29 iros.tex
@@
 Patient was in induced coma for around 1 month, and after that unable to walk, move, talk or swallow.
-After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.
+Throughout a first period of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia.
+%  which was very important in order to remove the feeding tube allowing her to start speech recovering.
 

### 2022-10-25 iros.tex
Added the IROS presentation

@@
 \author{%
-Franco Paviotti$^{1}$, Esteban Buniak$^{2}$, Rodrigo Ramele$^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
-\thanks{$^{1}$F. Paviotti is with Bioengineering, Instituto Tecnológico de Buenos Aires (ITBA)
+Franco Paviotti$^{1}$,  Esteban Buniak $^{2}$, Rodrigo Ramele $^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
+\thanks{$^{1}$F. Paviotti, $^{2}$E.Buniak and $^{3}$R.Ramele  are with Bioengineering, Instituto Tecnológico de Buenos Aires (ITBA)
                     Buenos Aires, Argentina
-        {\tt\small fpaviotti@itba.edu.ar}}%
-\thanks{$^{2}$E.Buniak is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires (ITBA)
-                    Buenos Aires, Argentina
-        {\tt\small ebuniak@itba.edu.ar}}%
-\thanks{$^{3}$R.Ramele is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires (ITBA)
-                    Buenos Aires, Argentina
-        {\tt\small rramele@itba.edu.ar}}%
+        {\tt\small \{fpaviotti|ebuniak|rramele\}@itba.edu.ar}}%
 \thanks{$^{4}$O. Freixes is with the CINER Centro Integral de Neurorehabilitación,
@@
 Therefore, the addition of an independent and new peripheral therapeutic signal, that can be assimilated as an extrasensory input~\cite{Brandebusemeyer.etal2021},  could improve dynamic balance performance on post-stroke patients which may have yet insufficiency to deal properly with the complexities of walking.
-Meaningful balance information, in terms of timing and location, can provide this extra signal in any form of stimulation, particularly vibrotactile feedback (VF).
+Meaningful balance information, in terms of timing and location, can provide this extra signal in any form of stimulation, particularly vibrotactile feedback (VF)~\cite{Islam.etal2022}.
 Although the effectiveness of biofeedback on static balance has been studied more extensively in the literature~\cite{DeAngelis.etal2021}, to the best of our knowledge works dealing with dynamic balance problems while walking have been more scarce.
@@
 The proposed development is implemented as a smart-vest~\cite{Brandebusemeyer.etal2021}, which we will call, \textit{Equilivest}, that address three possible clinical hypothesis of the underlying problem.
-We aim to provide motor learning, meaning to generate a fading compliant assist-as-needed vibrotactile feedback signal which is manifested to the patient as less conscious as possible~\cite{Srivastava.etal2016,Donato.etal2016}.
-The device aims to promote plasticity by producing timing vibrotactile stimulation based on kinematic and dynamics measurements.
+We aim to provide motor learning, meaning to generate an assist-as-needed~\cite{Balasubramian.etal2010,Maaref.etal2016} vibrotactile feedback signal which initially promotes voluntary control over movements of the joints~\cite{Islam.etal2022}, but which fades away to encourage automatism~\cite{Srivastava.etal2016,Donato.etal2016}.
+The device aims to increase plasticity by producing timing vibrotactile stimulation based on kinematic and dynamics measurements.
 
@@
 Patient was in induced coma for around 1 month, and after that unable to walk, move, talk or swallow.
-After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.
+Throughout a first period of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia.
+%  which was very important in order to remove the feeding tube allowing her to start speech recovering.
 
-After 7 months since event, the patient, was discharged from hospital and maintained a daily rehabilitation treatment, focusing on a remaining affection related to dynamic balance problems while walking.
+After 7 months since event, the patient was discharged from hospital and maintained a daily rehabilitation treatment, focusing on a remaining affection related to dynamic balance problems while walking.
 The patient achieved satisfactory index scores in static balance tests and is able to perform static hip-balance and ankle-balance.
@@
 
-However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or when concentration fades while walking, she is unable to keep up with the pace of the gait and the risk of fall increases.
+However, when the patient tries to walk on open-spaces, or with confronting lights (like walking towards sunlight), with other people moving around, or when concentration fades while walking, she is unable to keep up with the pace of the gait and the risk of fall increases, in a non-lateralized locomotion (symmetric)~\cite{Welniarz.etal2015}.
 Nowadays, the patient walks freely unaided at home but requires a Canadian cane otherwise and constant supervision.
@@
 \vspace{2pt}
-\caption{Survey and responses provided by his main patient's rehabilitation caregiver.}
+\caption{Survey and responses provided by patient's rehabilitation caregiver.}
 \label{tab:caregiverssurvey}
@@
 The IMU provides accelerometer and gyroscope data to get a 3-dimensional angular acceleration vector and a linear acceleration vector.
-Pitch, Roll and Yaw angles are calculated from a set of transforming equations and processed with a complementary filter which relies $0.98$ in gyroscope data and $0.02$ in accelerometer data~\cite{Fetick.2022}.
+Roll (Z), yaw (Y) and pitch (X) angles, aligned respectively with anatomical planes coronal, horizontal and sagittal are calculated from a set of transforming equations and processed with a complementary filter which relies $0.98$ in gyroscope data and $0.02$ in accelerometer data~\cite{Fetick.2022}.
 These values are transmitted by telemetry in real-time as UDP packets for off-board register, processing and further analysis.
@@
 This experiment aims to study the falling process.
-Participants are told to lean forward until they couldn't maintain balance anymore and let themselves fall into a mattress.
+Participants are told to lean forward performing ankle forward until they couldn't maintain balance anymore and let themselves fall into a mattress.
 This experiment is used to determine a threshold for the data that can help to identify the breakpoint conditions based on the IMU information where each subject falls.
 
-In order to test it, 5 healthy participants are recruited to perform 10 runs of falling situations  Participants wearing the vest  perform a one-step forward walking exercise with the upper-trunk leaned forward at different angles progressively until they can no longer cope with the unbalance situation and fall to the mattress.
+In order to test it, 5 healthy participants are recruited to perform 10 runs of falling situations  Participants wearing the vest lean forward by adjusting their ankle joint, without performing a one-step forward movement,  at different angles progressively until they can no longer cope with the unbalance situation and fall to the mattress.
 
@@
 This experiment has the purpose of analyzing and studying gait's behavior.
-In order to accomplish this,  5 participants are instructed to perform 10 sessions of walking in a straight line across ten meters, performing Ten-Meter Walking (10MWT) assesment~\cite{Olmos.etal2008}.
+In order to accomplish this,  5 participants are instructed to execute 10 sessions of walking in a straight line across ten meters, performing Ten-Meter Walking (10MWT) assesment~\cite{Olmos.etal2008}.
 We collected and analyzed pitch, roll and yaw values as well as angular acceleration changes registered by the IMU gyroscope.
@@
 The information provided from all the experiments allow us to implement three different VF strategies:  The first is an \textbf{Artificial Vestibular Feedback}, which provides information as a feedback for vestibular information integration process.
-This is implemented as a frequency-increasing VF signal that increases as long as the distance from the breaking condition position where the fall is inevitable decreases.
+This is implemented as a frequency-increasing VF signal that increases as long as the distance from the breaking condition position where the fall is inevitable, decreases.
 The purpose is to provide the patient with a continuous sensation that modulates the risk of falling.

### 2022-10-25 review/response.letter.tex

\documentclass[journal,onecolumn,12pt]{IEEEtran}

\usepackage{amsmath,amssymb,bm}
\usepackage{amsthm, amsfonts}	
\usepackage{cite}
\usepackage[normalem]{ulem}
\usepackage{color}
\usepackage{fancybox}
\usepackage{url,booktabs}

\usepackage{xr}

\title{Reply to Reviewer's Comments on\\
``Equilivest: A Robotic Vest to aid in Post-Stroke Dynamic Balance Rehabilitation'}
\author{}

\begin{document}

\maketitle
\pagenumbering{roman}
\setcounter{page}{1}

We appreciate a lot all the comments provided by the Reviewer.   Thanks so much.

In the following, we discuss our responses to pointed out issues.

\vskip+1ex
\noindent \dotfill

\section*{\fbox{Reviewer Transcript:}}

This work presents a device called Equilivest, a smart vest to support post-stroke patients with issues in dynamic 
balance by generating timing vibrotactile stimulation based on kinematic and dynamics measurements collected with an IMU placed on the torso.
The Equilivest addresses three possible clinical conditions. It can work as additional vestibular feedback to alert the user about a potential fall 
denoted by the crossing of a predefined threshold in trunk angle or/and acceleration. It can work as a gait pacemaker by suggesting to the user a 
normal gait pattern through vibrotactile stimulation. Finally, it can predict the risk of falling through a machine-learning approach on collected data.

\begin{itemize}
\item Could you clarify the following concept: “fading compliant assist-as-needed vibrotactile feedback signal which is manifested to the patient as less conscious as possible”?
\item It would be interesting to have more details about the impairment of the patient in your case study, does the impairment affect more one side of the body or is it general?
\item Could you provide a justification for the position of the IMU on the Equilivest? Is it based on literature or is it a practical choice?
\item The experiments in which the subjects are required to perform “falling situations” is not very clear to me, do they perform one step forward not to fall after 
bending the trunk or they first perform the step and then they bend the trunk? Maybe a video during the presentation could be useful.
\end{itemize}

\section*{\fbox{Reviewer Responses:}}

%\subsection*{\ovalbox{Reviewer 1 General Comments}}

Could you clarify the following concept: “fading compliant assist-as-needed vibrotactile feedback signal which is manifested to the patient as less conscious as possible”?

\vspace{10pt} 
\begin{quotation}
{\color{blue}

One of the aspects that was emphasized by the rehabilitation professional was to help with the patient relearning of the required movements to keep the balance or to recover a natural and automated gait movement.  Literature review emphasized two aspects to consider in biofeedback applications.   The first is the idea in rehabilitation robotics of \textbf{assist-as-needed} which is to provide only an external assistance when it is required and allow the natural development of the movement to develop as easily as possible and to have an active participation of the patient in therapy exercises~\cite{Balasubramian.etal2010,Maaref.etal2016}.

The second concept is the idea of to promote motor learning behaviour meaning to generate a vibrotactile feedback signal that initially promotes voluntary control over movements of the joints~\cite{Islam.etal2022}, but which fades away to encourage automatism~\cite{Srivastava.etal2016,Donato.etal2016}.

We have modified the abstract manuscript to clarify these concepts without using too much more space.  Thank you so much for the inquire.

}
\end{quotation}
\vspace{10pt}

It would be interesting to have more details about the impairment of the patient in your case study, does the impairment affect more one side of the body or is it general?

\vspace{10pt} 
\begin{quotation}
{\color{blue}
The impairment is not lateralized.  It does not affect one side of the patient, nor it is related to problems with one side of the vision field.  The patient can be in standing position without problems.  It can perform ankle-balance and hip-balance.  It can move in their own house unaided.  However, when confronting open spaces, crowded situations or walking towards lightsources, the patients needs to be very concentrated to be able to walk without falling.  When concentration due to fatigue or boredom fades, the patient start to stumble, gait becomes unnatural or forced and the risk of fall increases.  One aspect that the patient mentioned many times is that she can walk more easily along hallways, through narrow spaces with walls alongside.

Space permitted, we added some extra information in section II.A, and clarified the lack of lateralization.
}
\end{quotation}

\vspace{10pt}

Could you provide a justification for the position of the IMU on the Equilivest? Is it based on literature or is it a practical choice?

\vspace{10pt} 
\begin{quotation}
{\color{blue}
For practical choices at this stage of the project, we did our best to align the anatomical planes, coronal, horizontal, and sagittal with IMU's roll (Z), yaw (Y) and pitch (X) planes (Figure 1).  Yet we implemented a calibration procedure previously to each experiment with each subject.

We clarified the anatomical alignment in the manuscript.
}
\end{quotation}
\vspace{10pt}

\vspace{10pt}

The experiments in which the subjects are required to perform “falling situations” is not very clear to me, do they perform one step forward not to fall after 
bending the trunk or they first perform the step and then they bend the trunk? Maybe a video during the presentation could be useful.

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We appreciate a lot this comment, it was actually wrongfully explained in the extended abstract.  The experiment is a lean forward ankle-movement without any one-step forward.  Hence lower-limb and trunk lean forward until falling is inevitable and subjects fall into a mattress.

We clarified this in the abstract manuscript and we will add a small video in the presentation. Thank you for your suggestion.
}
\end{quotation}
\vspace{10pt}

\vskip+1ex
\noindent \dotfill
\vskip+1ex
\bibliographystyle{IEEEtran}
\bibliography{iros}

\end{document}

### 2023-01-16 iros.tex
Latest changes to submit the paper to arxiv.

@@
 Franco Paviotti$^{1}$,  Esteban Buniak $^{2}$, Rodrigo Ramele $^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
-\thanks{$^{1}$F. Paviotti, $^{2}$E.Buniak and $^{3}$R.Ramele  are with Bioengineering, Instituto Tecnológico de Buenos Aires (ITBA)
+\thanks{$^{1}$F. Paviotti, $^{2}$E.Buniak and $^{3}$R.Ramele  are with the Instituto Tecnológico de Buenos Aires (ITBA)
                     Buenos Aires, Argentina
@@
 %\thanks{*This work was not supported by any organization}% <-this % stops a space}
+\thanks{\textbf{This extended abstract was presented at the Workshop on Assistive Robotic Systems for Human Balancing and Walking: Emerging Trends and Perspectives at IROS2022.}}
+
 }
@@
 %Stroke is a medical condition that can affect motor function, particularly dynamic balance.
-Biofeedback can aid in rehabilitaiton procedures which help patients to regain lost motor activity and recover functionality.
-In this work, we are presenting a smart-vest device that assist in rehabilitation procedures by providing feedback in the form of vibrotactile stimulation.
-Information provided by principal caregivers, family, patient in the form of surveys and interview, is used to derive potential clinical causal hypothesis and these are used to drive the experimentation paradigm, and the robotic smart-vest to aid in the whole procedure...
+Biofeedback can aid in rehabilitation procedures which help patients to regain lost motor activity and recover functionality.
+In this work, we are presenting a robotic smart-vest device that can analyze Inertial Measurement Unit (IMU) data and assist in rehabilitation procedures by providing timed feedback in the form of vibrotactile stimulation.
+Information provided by principal caregivers and patients in the form of surveys and interviews, is used to hypothesize potential clinical causes and to derive alternative clinical procedures.
 %\end{abstract}
